\chapter{The dead Nazi Zombie}
\label{ch:The Dead Nazi Zombie}

%% Treffer am flugzeug werden per OLED Folie angezeigt
%% Das Flugzeug stürzte Nördlich von FN am => Meckenbeuren. Absichtlich so ferngesteuert
%% Bobo befreundet sich mit den Spielern, bindet sie in die Kinder Betreuung ein
%% Zitat Bobo "Du kannst nach Meckenbeuren gehen, aber dann wirst du sterben"
%% Archibald ist auf der Schussen Südlich von Meckenbeuren
%% Zwei Gruppen aus FN versuchen auch mehr heraus zu bekommen und es ist recht toxisch "Grauen Mäntel"und "Regenbogengrenadiere"
%% Es gibt ein Staatsbegräbnis für seinen Fliegerhelm
%% Ergebnis: Ein neues Narrativ finden, die Flieger einbinden => Clownstaffel der Lüfte


\section{Topic}

This is a criminal investigation in the entertainment "industry" in Friedrichshafen at the Lake of Constance.
The Norms have lots of entertainment and strange hobbies. In Friedrichshafen that turned into a Wrestling league styled air combat with two teams. On is the "Resistance", the other one "Nazi Zombies".
The planes they are using are electric and can be remote controlled to land when a critical hit is scored. They are designed after WW2 planes.
But being Norms they also do not really understand the real historical situation and the involvement of this town in war crimes.

The story starts when a plane is shot down "for real" and crashes burning into the Lake of Constance. Instead of just triggering the smoke machine and landing by autopilot on the "Loser Runway".
The Hero of the Nazi Zombie team "Herbert Hartfels, der Schlächter der Lüfte", flies a Spitfire.
His Nemesis a Messerschmidt (yes, they really know nothing about history).

The fights are a mixture of military pomp, Wrestling style Kayfabe with hero/villain stories, real action and technology (run by a small team of Pioneers).
The fans (especially the fans of the Zombie team) party in a violent soccer fans mode and those parties are feared by the population. But there are also fans who are able to tell you all the statistics baseball fans style ("64 percent of successful barrel roll escapes by Herbert are left").

There is a simulation league where beginners can train in simulators. They love that.

The job of the job of the protagonists is to solve the crime and try to sort out how Friedrichshafen can have a future with less historical ballast.

If the Protagonists already uncovered the Billionairs from outer space and learned that they have bunkers filled with weapons a "airforce" could be something they would appreciate to have as a backup plan....

The theme is "Never mess with dark history", "Know history, learn from it" and "Find your true purpose".

\section{What really happened}

No one knows who is playing Herbert Hartfels. People following Kayfabe tend to ignore that there is an actor/athlete behind this persona.
This actor once met a Lost travelling by pleasure barge over the Lake of Constance and the rivers attached to it.
The Lost was shocked by the Nazi Zombie show in Friedrichshafen and explained to the actor the historical links.
Understanding those and seeing the violence of the fans the actor decided to kill the persona. The only way out of this show business.

So he got one of the Pioneer mechanics "Sue" involved to plant a real bomb into the plane and add a remote control. He controlled the plane from a VR ground station (beginners league).
When the hit was registered, the plane blew up.

In preparation to that the mechanic and the actor did a prototype. The wreck can be found as evidence.

To complicate things: Another person saw parts of the plan and is blackmailing the Lost, the Norm and the Pioneer.

After the plane blew up, the actor wanted to find a new life. Do something simple and good. Like Clown doctor "Bobo the clown". This is how they meet him early in the adventure. Dressed for work in a public transport visiting children in different parts of the town. He will include them into his clown acts and entertain the children. The protagonists will not necessarily like it as victims of his pranks.

But with the blackmailing and the investigation the clown doctor will have to hide the tracks.

Can the protagonists uncover the truth ? How will they judge the pilot, and the blackmailer ?

\subsection{Timeline ?}

\begin{center}
    \begin{tabular}{|c c|}
    \hline
     When & What happened \\ [0.5ex]
     \hline\hline
     Day -99 & Up until now the pilot known as Herbert Hartfels is a kind of dark hero for his fans and does not analyse his role. \\
     \hline
     Day -98 & He sacrifices his plane in air combat and escapes by parachute, winds make him land some kilometers from the Bodensee where he meets a Lost \\
     \hline
     Day -98 to -50 & He regularly visits the Lost "Archibald"  to learn more about History \\
     \hline
     Day -49 to day -1 & He gets a trustworthy mechanic involved, the three (Herbert, Archibald and Sue) plan the death of the persona Herbert Hartfels. \\
     \hline
     Day -1 & The plane explodes, "Herbert Hartfels" "dies" \\
     \hline
     Day 0 & The protagonists are asked to investigate, and they meet Dr. Rednose Rupert [1ex]
    \hline
    \end{tabular}
    \end{center}

\section{Krimi: Beziehungs Modell}

\section{Krimi: Eisberg Modell}

\section{Krimi: Beziehungs Modell}

\section{Krimi: Location 1}

* Beschreibung
* Charaktere
* Hinweise (Beweise, Info, Beobachtung, Papiere, Mythische Info) - Red Herring Hinweise müssen zurück auf den Fall oder schnell in eine Sackgasse führen


\section{From the green zone (entry)}

\section{adventure acts}

\section{To the green zone (end)}

\section{NPCs}

NSCs müssen „Merkwürdig“ sein. Also mit Persönlichkeit

Krimi: Nscs mit Motiv, Alibi, Aussagen


\section{potential story hooks}

\section{Experience with player behaviour}

\section{Handouts}

%% Chandler Regeln für Krimis

%%    Glaubwürdigkeit des Abenteuers
%%    Technische Perfektion (der Mordmethode, z.B.)
%%    Realismus
%%    Muss spielerischen Wert auch ohne das Geheimnis haben
%%    Fokus auf ein Thema/Stimmung/Schwerpunkt
%%    Keine zu frühe Aufklärung
%%    Einfache Struktur, klare Lösung
%%    Ehrlichkeit bei den Hinweisen
%%    Logische Lösung
%%    Bestrafung des Täters (Justiz, Selbstjustiz, …)

%%%%%%%%%%%  sidebar box with links
\begin{sidebarBox}[title=Relics]
\hyperref[sec:Relic]{Relics} are objects or organisations from the past. They do not fit into the new world and will soon be dismantled. The list of relics to be dismantled is long. And some just keep on going until it is their turn. Or they fight back.
\end{sidebarBox}

%%%%%%%%%%%% For the index at the end:

\index{Billionaires from outer space}

%%%%%%%%%%%%%   For links:

\label{ch:Label name}

%%%%%%%%%%%  NPC

\begin{npcBox}[title=Leo]

    \begin{aspects}
    \item \aspect[High Concept]{An architect}
    \item \aspect[Trouble]{I will hulk out if you make me angry}
    \item \aspect[Aspect]{I dream of building big, but the situation keeps me small}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{3}
        \item \nskill{Athletics}{1}
        \item \nskill{Burglary}{0}
        \item \nskill{Contacts}{1}
        \item \nskill{Crafts}{4}
        \item \nskill{Deceive}{0}
        \item \nskill{Drive}{0}
        \item \nskill{Empathy}{1}
        \item \nskill{Fight}{2}
        \item \nskill{Investigate}{0}
        \item \nskill{Lore}{1}
        \item \nskill{Notice}{0}
        \item \nskill{Physique}{3}
        \item \nskill{Provoke}{0}
        \item \nskill{Rapport}{0}
        \item \nskill{Resources}{2}
        \item \nskill{Shoot}{0}
        \item \nskill{Stealth}{0}
        \item \nskill{Will}{2}
     \end{skills}

    \begin{stunts}
    \item \stunt{Improvising}{Leo gets a +2 to crafting when building architecture with alternative materials or scrap.}
    \end{stunts}



    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}
    An impulsive architect, he has a spire with a house on it. He is trying to cultivate the side of the rock by attaching small boxes for plants.
    He was part of the 5 minute riot that Kim escaped from. Being impulsive, he threw rocks at the three Project Lifeguard people. The cyborg followed Kim. A rock thrown by Leo hit an engineer, throwing him off a bridge and killing him. Sam, the third engineer, was hiding in their bunker. An antenna was destroyed by rocks thrown.
    After the rebellion turned bloody, Leo retreated. Shocked by his own actions.
    If this can be fixed, they can gain the support of a skilled architect who only lacks the tools to build fantastic vertical gardens and bridges.

    Leo is 60 years old and remembers the time before the disaster. He moved to Albstadt 2 years before the disaster. Leo studied engineering and architecture before moving there.

    \textbf{Location:} His own spire. With a small house (repaired). And a small hanging garden at the side of the spire (just some flower pots, he did not have the right tools for proper hanging gardens).

    \textbf{Problem:} Has to deal with killing someone. Maybe talking to Sam will help.

    \textbf{When convinced:} Can help build things (a real hanging garden, real suspension bridges, crab traps)
    \end{npcDescription}

\end{npcBox}