\documentclass{book}

\usepackage{../../static/templates/fate_latex_template/fate_solarpunk}
\usepackage{montserrat}
\usepackage{ebgaramond}

% For creating example text
% \usepackage{lipsum}

\title{Fate Solarpunk 2050 Lisbon Express}
\author{Thorsten Sick}

\pagenumbering{arabic}
\begin{document}

\chapter{Lisbon express}

\section{Overview}

The Solarpunk adventurers go to Lisbon as a family (all are married to each other) for vacation. The journey takes place with a long-distance train: A moving hotel with all amenities. The trip lasts 2 days and is an event in itself - not just a means to an end.

There will be murders along the way. The police will dock with an extra car, but the investigators will become victims themselves or will otherwise be prevented from investigating. The Solarpunks intervene.

The train won't stop anywhere until the murders are solved. Except at the terminal station. Such are the rules.

Playing time: a few evenings

\section{Topics}

Polyamorous Relationship:
All characters are intermarried. You have to arrange something. The norms only have one partner and the chain of events that starts on the adventure is triggered by that.

The children's theme:
They want to use the vacation to decide how many children they want to raise, how far apart the children will be born

Travel in the future:
A Solarpunk train as a rolling hotel with all amenities

Some Crime:
The murder is cleared up by the Solarpunks. Starts as a jealousy drama. Ends with more cover-up killings

Some horror:
The killer is an expert on this move. Knows all ventilation pipes, has all the keys. Is informed in good time about reconfigurations of the train and uses it.
But the first murder was in affect and sloppy. The others aren't that well thought out either.

Consumer vs. self-employment:
The Solarpunks are used to doing everything themselves. Here the system is built on service. This will cause trouble. In turn, fellow travelers are knowledgeable in their respective fields and can help solve some problems. As long as they are trusted, guided (as norms they are not really proactive) and still alive.
The norms are very powerful in a norm environment if they can use their apps and have AI connection!

Building a community:
The train is a closed environment. People in it a re suspects - and can be part of the solution. Every NPC can contribute to solving the mystery. But the protagonists will have to solve their problems first and forge a community.

\section{Departure}

It starts in the luxurious waiting room of the platform. The Solarpunks are all one family. Partly polyamorous connected. But also grandparents or godparents for the planned child. Because on the way to a holiday together in Lisbon (to see the wonders of the sea) they want to think about raising a child together.

You travel by train from Germany to Lisbon. The journey takes 2 days. The route with the most sights was specially booked.

The trains of the future are different. Their task is to ensure the most comfortable transport possible through Europe. Here high tech is hidden behind comfort. The trains are more like rolling hotels than means of transport. And they also have individual comfort cars.

* Dining car
* Private Rooms (Convertible: Sitting or sleeping. Each with shower and bath)
* Cinema hall
* Salon (books, bar) lots of fine wood
* Botanic (moving jungle wagon with glass walls and ceiling)
* Children's toy car
* Workout cart
* Wellness trolley (sauna, event showers, floating capsules)

Then you pack up and go on vacation to Lisbon

Since this is how you enter the world of norms as a solarpunk:

The train has its own (weak) AI. All amenities are controlled by a life tracker that the Solarpunks are loaned. They all only have "Guest" permission and don't know the apps. Are thus far inferior to the norms. The norms will almost unconsciously operate things on the train, switch gears, book (seats in the restaurant), ... For the solarpunks who approach the technology more directly, it's magic. And since the user guidance is unfamiliar (and permissions or apps are often missing), it is complex.

\section{To get to know}

As soon as they board, they meet a friendly Norm Investor and his wife. He calls himself "Dusk" after his role model, a billionaire who disappeared during the "Dirty Road to Eden".

She's coming with me. He himself likes to help the solar punks understand the life trackers. Voting takes place there (which film will be shown, car order, ...). As guests, they have less permission (rank 0: guest) than he does with rank 45. So they cannot control the sauna (if it is attached) beyond 60 degrees unless they have a medical certificate on the life tracker.

He himself is very amazed and pleased as soon as he learns that the characters have a polyamorous relationship with each other. The norms know that. But it is very uncommon. And he himself is in a phase where he and his wife are thinking about it. He needs advice. More precisely: He started an extramarital relationship on his travels. Already confessed to his wife. But the girlfriend doesn't know anything about the woman and he wants to use this trip to introduce them to each other and then extend the marriage to three people. But he still doesn't know exactly how to do it.

He also briefly shows them his lover *Dscharlien* (Lots of stickers from major conferences on his laptop. Plus pasted photos: his wife and his lover).

**Important** He unlocks his laptop and smartphone with his fingerprint.

\section{The first murder}


The victim does not know: The train attendant *Dscharlien*, who is his love, got on the train earlier this time. She had to change shifts and has already been there for 2 stations.

She wanted to surprise her lover. But then gets confused that he's there with his wife (she didn't know he was married). In the act, she stabs both of them with steak knives.

She takes the smartphone he has just been handling. And cut off his finger. The master control app runs on the smartphone, with which you can control the train down to the last detail.

But then she has to flee when she hears noises. another guest
It's one of the scientists. He finds the bodies. Doesn't give an alarm but steals the laptop.

The laptop is interesting for the scientists. But the murderess only wants the sticker on the laptop: your photo! She could reveal that. So now several factions are chasing after the laptop. Some because of the cold fusion. The killer because of the revealing photo.

After the murder, 3 things are on the train that are important:

* The laptop: Telltale sticker and when unlocked: Interesting data
* The finger. It's with the killer or in the restaurant truck refrigerator when she doesn't need it
* The mobile phone with the Master Control App

\section{appearance of the police}

Since everyone wants to go to the conference, we don't stop the train for the investigation. A police car docks. First the forensics team will inspect the scene of the crime (side compartment of the protagonists. They can simply enter the locked area through their intermediate door. To do this, they have to pick the lock).

The police will interrogate everyone. But the norms present also suddenly become very trusting. They want to find the laptop and think either the Solarpunks have it (they have similar devices) or they can help find it.

The police methods of the future are app based. The police and all potential helpers can send information, evidence and interrogations to a central police server via an app. There, an AI evaluates the data and shows live who is the most suspicious. The investigative activity is thus limited to collecting facts. And the players characters have the opportunity to determine themselves. Of course, all other suspects are also involved and informed. This creates the potential for manipulation.
Another problem with such algorithms are anomalies of all kinds. Things that are not common or unusual.

Since the player characters are strangers to the norm world and do not accompany a high rank in the app (probably just rank 0: guest) they are the most likely suspects according to the algorithm.

The police car is from a different manufacturer. It's the only place where Dusk's Master Key has no influence.

\section{technology}

\subsection{train}

The train is electric and powered by catenary (important in case of rooftop chases).

Each car in the train has its own controls and drive. After coordination among the passengers (or as needed), one of the cars can pull out, go to a siding and dock somewhere else. Cars can also be requested at a later date. Quote: "Attention, please stay in your car. The doors will be locked. The car order will now change according to your wishes."

The staff should act inconspicuously on the train. It does that too (beds made while you're gone, ...).

There are staff doors (only used by staff). But also in many cars under the floor crawler gears for the technology. Sometimes under the covers too. An alien horror feeling is therefore quite possible.

The car order can be important for the investigation. Tip: Draw a floor plan for each wagon. If the carts rearrange, rearrange these floor plans on the table as well.

The wagons are approx. 25m long and 3m wide. Wagons can be two-tier. Or one-story with lots of air.
The passage from carriage to carriage is centered. Depending on the content, the aisle in a trolley can run sideways or even on the 2nd floor.

Each trolley has all the hardware integrated that is possible for its type. However, not everything is paid for and booked by the railway company by default. However, these features can be unlocked with the Master Key (which is on Dusk's phone).

Anyone on the train can book normal services via an app (although the Solarpunks have lower rights).
Something like "Order a movie in the cinema and book the hall for 22:00-24:00".

\section{The wagons}

Each car has enough battery for a few kilometers. And can - if there is an overhead line - draw power from it. Each car has its own drive and control. Can therefore separate from the train, on the neighboring track. Overtake the train and cut back in at another point.
Or get off the train and head for a station.

\subsection{Sauna trolley}


Amenities:

Sauna area, showers and two floating pods. The sauna gets a maximum of 60 degrees without a medical certificate on the mobile device (and the protagonists probably don't have that).

hidden:

Under the ceiling formwork are two robotic arms to move the heavy water pods. A side wall of the cart is also slide-away. Over the side, the robotic arms lift the pods off the train so they can be serviced and cleaned.

Unpleasantries:

The sliding side walls and wild robotic arms emerging from the ceiling are a nasty surprise.

Murder Options:

As a train attendant you can set the sauna to pyrolysis and thus eliminate a corpse. This setting is not even visible to everyone else.
Pyrolysis stinks. Can be interrupted with hacks and a briquette remains.
You can also lock one of the floating cocoons with special rights ("Maintenance!" as an indication)

\subsection{botanical}

A moving jungle. With glass walls and glass ceiling

Amenities:

A winding path sprinkled with wood chips winds its way through a jungle: laid out as picturesquely as possible in the railway carriage. Some moss cushions invite you to sit.

hidden:

Unpleasantries:

The car has a spray mist irrigation system. If you hang the dishwasher (from the dining car) on the fertilizer supply you can fill the room with toxic fog at any time with the master key.

Regarding the cleaner: They are genetically optimized bacteria. Dishes are machine washed at 35°. A drop of the cleaner is added and the bacteria multiply, eating dead organic matter. After a few generations (minutes) they die off. You can't help it. By then, however, they have decomposed the leftovers and the remains can be easily rinsed off.
There's an antidote for accidents in the kitchen.

If an entire bottle is nebulized and people are standing in the fog:

* It will be one of the meanest scrubs ever. But no more. Light consequences as a maximum
* All organic clothing items are dissolved into Schlonz
* Are the dead parts of the local plants (bark, ...) also dissolved. Everything here will die.

Murder Options:

This car has as much confusing jungle in a small space as possible. The path is tortuous. You can easily bury a corpse in the humus. Possibly also hang in the crown of one of the trees.


\subsection{Dining car}


Amenities:

There is not enough space for all travelers at once. But the protagonist group plus some other guests can sit at the beautiful tables and have a rich choice of food. Booked via app. Higher ranks beat lower ones.

hidden:

A surprisingly large part of the car is the kitchen. However, the car is designed in such a way that as a guest you only really notice the counter and overlook the rather hidden door for the staff.

Unpleasantries:

Part of the dining car is an automatic kitchen. It could be sabotaged. Then only people who can cook will get food if they hijack the kitchen. So norms will starve.

Murder Options:

Poison, knives, automatic food processors, grease and steam.

\subsection{private rooms}

(Convertible: sit or sleep. Each with shower and bath)

Amenities:

Each room is small but can be converted into many configurations thanks to smart furniture. Bedroom, sofa circle, sofa with screen and game console, empty, ...

When the sofa is folded away, you can take a shower in the room. Only the toilet is in a separate room.
There is enough space for 4 people.

There is a minibar. game console. TV

hidden:

The configurability is only possible through the spaces in the walls. And here you can secretly walk through the train along the whole carriage. If you know this trick.

Unpleasantries:

With the Master Key, you can override the resident's configuration program and have a poltergeist-esque situation where the automatic sofas try to crush people. Completely detaching the animatronics helps.

Murder Options:

The attacker could come out of the walls. The room was not designed for safety.
Or override the sofa animatronics and crush the residents.

\subsection{Dusk's car}


A specially prepared passenger car with extra large rooms and a lot of luxury. Can't enter while Dusk is alive and the police will seal it off right away. You also need the master key. Or a police key.

\subsection{cinema hall}


Amenities:

You can watch practically any film on a large 3D screen. The sound system is stunning. A small snack machine delivers paper bags with sweets and drinks.
Registration via app. Higher ranks take precedence.

hidden:

Unpleasantries:

Murder Options:

\subsection{Salon (books, bar) lots of fine wood}

Amenities:

There is fine liquor (whiskey, gin, wine) self-service and rows of books. The latter are paper specimens and the bookshelf is only the visible part of a larger robotic warehouse. The content can be rotated if desired.

If a book is not available, a digital version can be loaded onto one of the e-books.

Wing chairs and sofas are distributed throughout the room.

hidden:

There are a surprising number of crime novels in the camp. Many were read on the last trips and *Dscharlien* murder sites were marked. Here she learned to kill.

Unpleasantries:

???

Murder Options:

The robotic book storage in the walls offers (uncomfortable) space for one person (living or dead). Here you can hide or listen to conversations (possibly also with a recording device).

It may well be that many people use this room for discussions because it is clear and homely.

\subsection{lounge and disco}


Amenities:

There is a large disco ball, lasers and smoke machines. In addition, some armchairs (foldable from the wall) for more comfortable music. A dance floor and a cocktail bot.

The music is determined by the people with the highest rank in the app.

hidden:

The Cocktail Bot mixes cocktails from 12 visible bottles. But in order to be more flexible, it has space for many more ingredients behind the casing. It could also be poison.


Unpleasantries:

You can confuse with lasers and fog. Or when the disco is parked next to the sleeping car, terrorizing those sleeping there with music.

Murder Options:

Poison in the Cocktail Bot. The corpse could be hidden behind the sofas that slide into the wall.
It comes to the fore when you switch the wagon from disco to lounge and the sofas slide onto the dance floor.

\subsection{children's stroller}


"There are no children traveling with you. But the compartment is needed in Lisbon. That's why it's going with you."

Amenities:

There are children books, toy boxes and a fully automatic, reconfigurable climbing frame.

hidden:

Unpleasantries:

The Master Key can also be used to reconfigure the jungle gym while people are in the room. And then drive the servos into areas that are not safe....

Murder Options:

The scaffolding can crush and tear people. Of course there are guarantees. And you can only bypass them with the master key...

\subsection{workout cart}


Amenities:

Some sports equipment is set up here. These can also be configured via servos. A lot is gameification and fun. For example the VR area with haptic feedback and the four-directional treadmill.

There are no weights. Instead, you work against robotic arms and winches.

hidden:

There is a small medicine cabinet and the couch can be converted into a sick couch. With the bikes/ergometers and sensors here, a doctor can also carry out a health test for the solar punks and thus unlock some things for them (sauna to more than 60 degrees).
One of the fellow travelers is a doctor (has 2 years of training, the right to carry out the tests and the right apps).

Unpleasantries:

Murder Options:

Here, too, you can use the master key to direct the sports equipment (which are practically robots) against people.

\subsection{Railcar/Loc}


No access for guests. Has its own batteries to pull the whole train. Runs fully automatically, but has its own driver's cab (for difficult situations or enthusiasts who want to drive - this requires the Master Key).

hidden:

In order to be able to fend off raids by the Lost, here are a shotgun and a pistol with ammunition in a locked gun cabinet.

Unpleasantries:

A modern pilot's cockpit with touchscreens. Without a pilot. The chair is very comfortable. And there is a personal coffee maker.

Murder Options:

The only dedicated weapons are here in the room.

\subsection{Recycling and technology wagon}


A central trolley for recycling, water treatment, expansion batteries.
No access for guests.

Amenities:

No. At least everything is clinically clean and tidy here. With all the tanks and shredders.

hidden:

Unpleasantries:

Murder Options:

You can make bodies disappear here. In the shredder.

\subsection{Special: gliding}


Dusk ordered it specially. In places where there is no overhead line, you can be pulled up 200 meters on a kite glider using the winch and watch the train and landscape from above.
Dusk intended to do this especially on coastal tracks.

Amenities:

You can see the most amazing sights from above.

hidden:

Nothing hidden. A carbon nanofiber rope holds a steerable kite. The winch is controllable from the kite and the rest of the car is runway. The roof of the car can be completely slid away.

With the master key you can of course control pretty much everything from below....

Unpleasantries:

From the kite you can theoretically inspect the rear cars from the side while flying low. That's quite a stunt, despite the support systems.

Murder Options:

You can quickly store a corpse on the unrolled dragon.

\subsection{The conference}


It's a technology conference. Most of the participants are from the classic energy sector (solar, wind, biomass, water). But other related subfields also attract people. Geneticists are also interesting because of biomass-consuming microorganisms. Or roboticists for the automation of the systems.

Dusk wanted to find new partners here.


\section{Fellow travelers and other NPCs}


As with Werewolves of Mirkwood, many of the fellow travelers are connected and one murder could set off chain reactions. "If A is murdered, B begins to suspect C".

Many are also interested in the contents of the laptop.

What the other travelers won't do: Injure or kill each other. They're normal people.

\subsection{Prof Benschamin}

He travels as a researcher in cold foot to Lisbon for a congress. He is very introverted and mostly in his compartment. A doctoral student *Tscharlie* is the first point of contact and "secretary". That makes him very mysterious.

The cold fusion is a hoax. 10 years ago he invented improvements to an inverter design (+0.5% efficiency !). But these were stolen by Dusk.
Now he wants to set a trap for Dusk and have the cold fusion stolen from him. And then damage Dusk by blowing the hoax. That will cost him his own reputation. But it's worth it to him.

Once Dusk is dead, the only thing left for him to do is get to the laptop and possibly find evidence that Dusk cheated on him back then.

He could help with all electricity problems around the train (batteries, overhead lines).

\subsection{Prof. Firenze and 2 students}


The professor (visibly trans) cares a lot about her students. They will hold a poster session and will also practice this on the train. The Solarpunks could become "victims".

A student is relevant: Louis is a courageous student with political parents. He promised "Dusk" in a letter and in a clandestine meeting on the train: If Dusk refrains from sacrificing a reforested forest to a large solar farm (and building on the less-than-viable alternative site), that he would once have influence on Dusk's behalf with his parents. The letter is in Dusk's car.
"Dear Mr. Dusk. I am on the train with you and I have an urgent request that I am sure you can fulfil. In return I am sure I can help you. My parents are influential politicians in Europe. I will address you later and we think so both will benefit. Signed: L."

Name of the other student: *Elise*

Louis wants the laptop now so that he can stop the construction in Wlad.

\subsection{The policeman "Leon"}


Will come later and couple his police car to the train.
Leon is addicted to alcohol. This is also recorded in the app and he is not allowed to drink a drop. With the stress on the train, all the alcohol (salon, disco, dining car, private room) is very tempting. Since it is all inclusive here, drinking would not be recorded. So over time, Leon will turn to alcohol more and more.

His natural enemy here is Dr. Med Frieda, who could recognize and enter his condition. Then his relapse would be on record. He's aware of that too.

He wants the laptop as evidence

\subsection{dr Med Frieda}


Doctor of medicine. Can heal many wounds with her app and equipment adapted to it (is in the workout cart) and also certify health (important for using the sauna and for unlocking the really hard equipment in the workout cart).

She doesn't want to go to the congress in Lisbon, she just wants to go to the sea and visit friends.

She doesn't want the laptop. But maybe someone is hiding it in their compartment.

\subsection{Actor "Williams"}


Is the attraction on the train. Everyone is attracted to him. Even Dusk is fascinated. And also happy not to be the sole focus.

Williams, however, has a secret love that doesn't do much for his public image. He's a railroad nerd. Actually, he would like to look through all the crawl spaces, all the cable channels, ...
But nobody can ever find out. Because that would damage his image of "dumb and tough". He tries to keep this up. But actually he is smart, educated and curious. Especially on trains.

Dusk is known for being a bit dated - when it comes to politeness. That's why he wrote a letter to Dusk.

"Dear Mr Dusk

I am turning to you with a request. There is a deep need within me that I'm sure you can understand and probably satisfy. In order to explain this in more detail, I would like to meet you for a champagne - also to celebrate the approval of the series 24 A locomotives. Kind regards, Roland Ehrlich"

He can become an important resource for the protagonists. Just different than one might expect from his films. He is familiar with the plans and background of all cars. Couldn't fix, hack or modify anything though.

Wants the laptop because of all the great train plans!

\subsection{Jarlia}


The killer.




\section{characters}



\section{End}


Should the characters arrive safely in Lisbon, they will find a beautiful city on the seashore. Retrofitted to Solarpunk with lots of greenery.

The mountains of the city are manageable thanks to e-bikes.

You can rent boats and take a little trip out to sea. To the solar and algal fields just beyond the visible horizon that feed the city.

\end{document}