\chapter{Character creation}

This source book is based on FATE Condensed (https://fate-srd.com/fate-condensed). It offers simple rules but still the option to play a complex campaign.

For fast fun you can simplify by using FATE Accelerated.
Or add more rules from FATE Core and the extensions.

To build a character using the Condensed rules:

\begin{enumerate}
    \item Pick a faction
    \item Pick a profession or specialisation
    \item Get inspired by the philosophies
    \item Now start adding the Aspects
\end{enumerate}

\section{Special rules}

\subsection{New skills}

Each faction has access to a unique skill. On character creation you can pick it like any other skill.

\begin{itemize}
    \item \hyperref[sec: Lost]{Lost} are skilled at survival which is covered by their skill \hyperref[sec: Bushcraft skill]{Bushcraft}
    \item \hyperref[sec: Norms]{Norms} have years of experience using their Hive controller which is represented by the \hyperref[sec:Hive control skill]{Hive control} skill
    \item \hyperref[sec: Pioneers]{Pioneers} are masters at improvising technology by using their \hyperref[sec:Prototyping skill]{Prototyping} skill
\end{itemize}

\subsection{Supporting stunts}

Fate contains several stunt templates. At the heart of Solarpunk there is the concept of building societies and supporting each other. This is why another stunt template is available:

\begin{itemize}
    \item Because I am a gun nerd I can create a boost for person's shooting action when I have the opportunity to give some advice (Example: "This is one of the gun models you should hold with both hands")
    \item Because I am socializing while cooking I can create a boost for the people skills of one of the people taking part in cooking (Example: Cooking with two enemy parties who should make peace)
    \item Because I am a a athletics role model I can create athletics boost for someone following my example (Example: the person climbing up the rope second)
\end{itemize}

Those boost are limited to a skill or use case and are not as general as a standard boost. And they always boost someone else.

% Original: Because I am a Smooth Talker, I get a +2 when I Sneakily create advantages when I’m in conversation with someone.

\section{Dark past}

This is optional: To add more depth, add a Lemming past. Most of the people alive in 2050 started as a Lemming. Some shock made them pick a new, more sustainable, philosophy. Either Norm, Lost or Pioneer.

\begin{enumerate}
    \item What was your life as Lemming ?
    \item Did you have a job that can still perceived in your behaviour today (teacher for small children, preacher, bureaucrat)
    \item Did you do anything you now regret ? Have you been on the wrong side of history ?
    \begin{enumerate}
        \item A bureaucrat slowing down progress ?
        \item A police officer beating down the first buds of the Solarpunk revolution you are now part of
        \item A politician taking bribes to keep fossil business alive ?
    \end{enumerate}
    \item What happened to make you change your mind ?
    \item Do you keep your past life a secret ?
    \item Do you accept what you did ?
    \item Do you try to fix the damage your old self caused ?
\end{enumerate}

Please discuss with your group first if you want to add the extra darkness in case of using sins-of-the-past. And if you do: Create own story lines for the characters with those sins. Make the characters "pay" for what they did. But as this can break the Solarpunk vibes. Only do that if you are really good at steering a positive Solarpunk story. This means: Not in your first campaign together