\section{Teaser}

Solarpunk 2050: A FATE Setting - It's the year 2050. The climate catastrophe has caused millions of deaths and destroyed society as we know it. But the Solarpunks have saved humanity. And although now everything could be fine . . . it is not.

What would once be the Solarpunk movement is fractured.

The \textbf{Pioneers} live their hyper-progressive individualistic technology utopia while the \textbf{Norms} live in hive cities in an AI controlled environment as a collective society. And the \textbf{Lost} decided humanity should have ever been so dependent on the newest technology.

In this game the players can play characters of any of those factions and together build a new utopia - which would be simple if they could agree on one.

\begin{pioneertalk}[title=Pioneer Photovoltaik site]
    Well folks. Unpack the soldering irons. We need a new autonomous solar farm for community expansion.
    We have 10 laser welding machines. Fits perfectly - there's no dispute this time - all the children can help stand up the solar modules. Who is securing the perimeter with the drones today? Yesterday someone heard diesel engines in the forest.
\end{pioneertalk}

\begin{pioneertalk}[title=Pioneer Photovoltaics site - later]
    \begin{itemize}
        \item \npcquote{Drone Pilot}{Folks, I don't see any casualties, but we have a problem}
        \item \npcquote{Benjamin}{Are the children okay?}
        \item \npcquote{Drone Pilot}{Yes. No one was hurt. 10 with laser welding devices, 5 with their child-sized exoskeletons constructing the solar modules. But they 're doing too well.}
        \item \npcquote{Benjamin}{?}
        \item \npcquote{Drone Pilot}{From above, the modules look like a giant-you-know-what. TTP of 5 hours is impressive perfomance. But I'm for house arrest}
        \item \npcquote{Benjamin}{I wouldn't give one for that. When I was young I went through a phase where I drew stuff on bus stops with permanent markers}
        \item \npcquote{Drone pilot}{But you can see it from space !!!}
        \item \npcquote{Drone Pilot}{... Tonight at the community meeting. We need to talk ...}
    \end{itemize}
\end{pioneertalk}

\begin{normtalk}[title=Party chat]
    \begin{itemize}
        \item \npcquote{Tscharlien}{Found something in an underground forum. For the episode 5 season 6 of Woodland Village you should buy the Mykonos inc red wine, the Mykonos inc olives (black) and the Mykonos inc feta. Why it didn't say.}
        \item \npcquote{Mischell}{I read that too. Unfortunately did not do that.}
        \item \npcquote{Kewin}{I saw that too. Why should I have done that ? Missed the episode.}
        \item \npcquote{Tscharlien}{That was so awesome!!! It was so great! The gang in the episode sat there at the table in this fine pub between 1:45 and 2:15 and ate exactly the same things! I felt like I was there!}
        \item \npcquote{Mischell}{I saw that too. Will always regret not belonging to the underground forums inner circle.}
        \item \npcquote{Marwin}{You are aware that this was a marketing stunt ?}
        \item \npcquote{Mischell}{Do not spoil the fun. I know. I even know the team who did that. They promised to weave the series into reality even more. "At a level no one will expect to be possible".}
        \item \npcquote{Tscharlien}{This is art. Like the Banksy monument in Moskow}
        \item \npcquote{Mischell}{...or the solarpunkified pyramids in Egypt}
        \item \npcquote{Marwin}{But that made a lot of people angry}
        \item \npcquote{Mischell}{The only angry people were Lemmings. The locals liked that it respected the traditions and the ancient Egyptians who built the pyramids would have loved it}
    \end{itemize}
\end{normtalk}

\begin{losttalk}[title=Council of war]
    \begin{itemize}
        \item \npcquote{Brutus}{According to our scouts, the Pioneers are celebrating their new crazy thing: a giant Solar ...symbol of fertility ? While the weirdos are distracted, we'll raid the Norm City}
        \item \npcquote{Achilles}{A what ?}
        \item \npcquote{Brutus}{The Plan: Motorbike Phalanx to the marketplace. Artillery at the city limits. Flanking from Greengate Park and from the ice cream parlour.}
        \item \npcquote{Achilles}{By the way, the can artillery people are sober again}
        \item \npcquote{Brutus}{Good}
        \item \npcquote{Brutus}{Then we'll get the most important BBDs out with the trucks and be gone within an hour. By then the police will arrive from the next town or so.}
        \item \npcquote{Achilles}{How much beer, beans and diesel can we get in the truck in an hour?}
        \item \npcquote{Brutus}{...is 5 years in a row already a tradition ?}       
    \end{itemize}
    The conversation is interrupted by a test shot from the can artillery hits the tent. No injuries        
\end{losttalk}


\begin{normtalk}[title=Defenses]
    \begin{itemize}
        \item Dehnis is sitting at his favourite place. The park at the beach in the city. Watching the river flow by. He checks the progress bar in the AR view of his Hive Controller. The drone will deliver his free coffee and cake in 74 seconds.
        \item \npcquote{Supervisor}{Chief Inspector Dehnis? The Lost are attacking the city. Your troops have order to retreat so as to not to further provoke the Lost}
        \item \npcquote{Chief Inspector Dehnis}{Understood}
        \item \npcquote{Supervisor}{Are the warehouses sufficiently stocked with diesel, beer and beans?}
        \item \npcquote{Chief Inspector Dehnis}{Yes}
        \item \npcquote{Supervisor}{Well, then it should be over soon. By the way, reinforcements are on the way. Meets in 1-2 hours}
        \item \npcquote{Supervisor}{And make sure the Pioneers don't interfere. If necessary, encircle and seal them off. They will try to save the city again. I don't want to have to work overtime today.}        
        \item \npcquote{Chief Inspector Dehnis}{...is 5 years in a row already a tradition ?}
        \item \npcquote{Hive Controller} Dehnis, please prepare for delivery.
        \item Without looking, Dehnis reaches out and the drone drops the parcel right into his hand. Coffee and cake. Just what he needs right now.
    \end{itemize}
\end{normtalk}


\begin{pioneertalk}[title=Gathering]
    \begin{itemize}        
        \item \npcquote{Bernd}{Guys, short party break. The city is attacked by the Lost. We'll have to save it. The police have cordoned off the streets. We race through the forest with the e-bikes.}
        \item \npcquote{Bernd}{The ticket system is currently being updated. Everyone who wants to join assigns to one of the five teams. Details are in the system.}
        \item \npcquote{Bernd}{The Lost are after BBDs. In addition to protecting people and the city, we ensure that the diesel tanker does not leave the city.}
        \item \npcquote{Bernd}{The tanker must not burn out under any circumstances. The last time we compensated CO2 for 2 years. And that's why Team Five is the Hazmat Team. Only people with the necessary training can register there. This team always stays with the tanker. Don't forget the equipment!}
        \item \npcquote{Bernd}{Well. The task tickets are online. Everyone takes up to three tickets with tactical objectives and let's go.}
        \item \npcquote{Bernd}{The rest keep partying. We'll be back in three hours at most.}
        \item \npcquote{Bernd}{I'd call 5 years in a row a tradition. Have fun.}
    \end{itemize}
\end{pioneertalk}
