\section{Global south}

This is not playable yet.
The reason why I already added it is to create a complete picture of the world.

The global south is not reachable by the rest of the world. The satellites are down. There are sometimes manually generated network connections but no one had the time to travel there. Everyone assumes that those regions are uninhabitable to human life thanks to the climate catastrophe. Which ist true.

But the people on the global south managed to science their way out of it. Their tech level is the highest of the world. And they are keeping it secret. Assuming that the rest of humanity is not ready yet (prime directive style).

The reason for their high tech level is their ability to store a memory matrix of human minds and ask them for advice ("the ancestors"). They picked those minds of volunteers wisely and those memories are constantly developing new technology and social and other progress. Without that they would perish - thanks to a hostile planet.

Their problem: An almost alien planet
Their solution: Transhumanism, geoengineering, gen editing (crops, wildlife, humans). For other humans it looks like superpowers.
The problems this causes: Many. Including a disconnect from their history, humanity and things
Solutions to that: Clinging to traditions, rituals and society like it is the last lifeline to stay human

Connections to rest of the world: Managed. Everyone outside thinks they are shattered. For that they also have visitor towns they show to foreigners. But they are also supporting outsiders through the UN. And sometimes they send spies/missionaries/agents called "drifters" to other parts of the world to seed some advice and help others grow. Spying wise they just want to know: where are the problems of that area and how can they help. And maybe if there is a problem brewing that has a blast radius large enough to also reach them.

They are not the bad guys ! They struggle to survive. And finally just want to be left alone - and decide who, when and where to contact.

Sometimes they reach out to the global north and "collect bright minds". It is an honour to be collected.

The mind is not altered. No one is harmed. The machine just generates a snapshot which is then run on a server somewhere in the global south.
The collectors will travel to the global north and try to explain to the chosen person how the global south really looks like and what a mind-copy is (both things extremely hard to explain). If the person volunteers he/she will travel to the global south for the copy procedure. Afterwards there are two identical minds - one biological and one virtual.
The visiting volunteer can the travel back to their home country after vowing to never tell someone about their trip and the real situation in the south.

The virtual can instantly start to confer with the other bright minds.

As the people of the global south fear for their "humanity" with all the drastic changes they have been through many technical operations are wrapped in rituals like "Meet the ancestors". To keep the culture intact. They are totally aware of the technical background and why they are intentionally keeping the culture alive in that way. No Warhammer 40k Omnisiah/Machine spirit stuff here. But it may look like that sometimes.

Space travel: Nope. But they could as only faction build a ground to space laser to blast holes into the Kessler Syndrome. But why ?
