\chapter{Factions}

There are three major playable factions in the Solarpunk world. Each has its own unique approach to life.

\begin{itemize}
    \item The creative and forward pushing Pioneers
    \item The Norms, who draw their strength from cooperation as a collective society and AI coordination.
    \item The Lost. Digging in the ruins of the old world and improvising with the old technology.
\end{itemize}

These factions are not enemies. And a successful team will probably need members from all three factions. But there is always some friction between the different approaches these factions have to life, the universe and everything.

The reduction to three factions is not the whole truth. In 2035, the faction construct was created by sociologists using cluster analysis to somehow label modern societies. There are even more factions than that if you start counting the small and odd ones.

The factions are also fluid. Members of a family may belong to different factions. Or a person may move from faction to faction as their outlook on life changes. This is not a big deal.

Factions are not strictly defined. There are hundreds of different Pioneer communities, each with their own approach to experimenting with a possible future. Hundreds of AI-powered cities where the AI will shape society differently because of the local definition of a "happy life". And many Lost Families who have found their own way to survive and thrive in the wilderness.

GMs and players: Create your own !

The Solarpunks: This game is set in the midst of the Solarpunk revolution. No faction can call itself Solarpunk. Each lacks some of the core principles that make it Solarpunk. But if the factions were to combine their strengths, they would evolve into a Solarpunk movement. This development could happen in the group of protagonists, in the communities they create and in the people they meet.

Because:

\begin{itemize}
\item The Lost lack the openness and progressive spirit of the Pioneers.
\item The Pioneers lack the wisdom of the past that the Lost collect.
\item The Norms lack the spirit and curiosity of the Pioneers.
\item The Norms could teach the individualistic Pioneers a thing or two about cooperation.
\end{itemize}
