\section{Lost}

The Lost are the fraction that did not join the others on the "Dirty road to Eden". They quite early realized that some horrors will be involved in achieving a Solarpunk utopia. And they did not want to pay the price. This fraction is the only one not actively denying what happened.

Their approach is to life in and from the ruins of the Lemmings civilsation. The reuse the old technology and enhance it. This is what their cloths, tools, vehicles and housings are made of. Old tech reused in a creative way.

Living in the ruins they developed combat and survival skills and are experts in exploration.
Many historians are in their ranks.

They do not necessarily trust the Solarpunks or the Norms. Because they still remember the "Dirty Road to Eden" pretty well.


\begin{warning}
    Details below are old and not in sync with the new concept. After discussion and experiments they will change
\end{warning}


\subsection{Profile}
\begin{itemize}
    \item Class: Might of the strongest. Through competitions
    \item Advancement in society: Through raids, organizing resources (especially fuel and old spare parts)
    \item Political System: Military / Spartan inspired
    \item Company form: tribal society. With bloodlines. External people are robbed. That can also be in agreement then it's more of a ceremony.
    \item Conflicts: fights for rank - sometimes at the expense of outsiders
    \item Appearance: Military clothing, body armor, pads. Short hair
    \item Taboos: showing weakness, accepting new things
    \item Language: Short and military
    \item Tendencies: Conservative, fatalistic, aggressive, destroyer
    \item Law: * Judge: The leader * Penalties: Corporal punishment up to the death penalty. Atonement through risky action possible
    \item Corruption: Yes
    \item Weapons: Homemade firearms, rockets and clubs. Weapons are often just as dangerous for the wearer as for the target.
    \item Architecture: wagon castles, corrugated iron shacks, trailer parks
    \item Vehicles: Diesel powered. Massive and heavy. Keep old technology alive with repairs.
    \item Resources missing: Diesel and old spare parts
    \item Party: Loud, Hard. Leaving behind alcohol, guns and rubbish. Out of principle. Intentionally so that it's all about that around. Fireworks
    \item Success: Leaders of big raids, groups with the baddest vehicles,
    \item Drugs: aggression-increasing and disinhibiting. Often stuff mixed with alcohol. Unplanned and dangerous experiments are the order of the day.
    \item Psychotherapy: Weakness does not exist. This is why therapy doesn't exist
    \item Media: The Lost run pirate channels to broadcast their view of the world (often hatred, half-truths, and misunderstandings of science).
    \item Education: essentials (reading, arithmetic) for 4 classes. No education whatsoever, very little history or culture. Shooting, welding and driving is learning-by-doing once you are considered mature. Anyone can "teach". . .with corresponding results.
    \item Coordination: Tribes and small groups are ordered around by their respective leaders.
    \item Diet: Grilled meat (sometimes roadkill-grilled-on-an-old-oil-drum) and "classic food" from the 1990s. Like hamburgers, fries or hot dogs from the microwave
    \item Names: generals. People from History: Brutus, Hannibal, Ramses, Alexander, . . . Often not so wisely chosen. Brutus, for example, is the son of the prodigal Caesar. . . .
    \item Gendern: Quote: “If I say \bf{men !} women are automatically meant as well"

\end{itemize}

Haven't adapted at all. Climate change doesn't exist. Despite daily evidence. Are structured like sects. Drive combustion engines and no longer get spare parts for them. Gas is incredibly expensive. It's always everyone else's fault. Quote: “This dog tastes like the best steak. Back then, boy, we ate something like that every day." What between Mad Max (mechanically patched vehicles), terrorists, street gangs, oddities and sect. The rest of the population feels sorry for them when they don't fear them. You can roam the cities mobile or have a settlement somewhere like "Diesel Heaven". Your life is self-chosen terrible. But if they were to adapt, they would have to admit that their world view was wrong for decades. Quote: "Yes, because of the paved parking lot my basement waters every year, but where else should I park my SUV?" There are some who proclaim kingdoms themselves and pay with their own currency (usually the name contains "Mark") . Another problem
with the Lost may stem from their desperation - or the leaded gasoline they use: They tend to have an increased potential for aggression.


\subsection{Relationships}
Among the lost, an accepted relationship is limited to "father-mother-child(ren)". This often causes fractures and personal unhappiness.

\subsection{The Mystery of the Lost}
No one, including the Lost, is really aware of the important niche the Lost occupy in the ecosystem. Areas where the Lost have been completely driven out are soon overrun by mutated animals.
For the Lost are the Alpha Predators with no exquisite taste in flesh. They hunt the giant bred rats, dogs and cats for consumption. They cook them at the campfire. Add beer and beans.
This keeps the animal population small. The Lost don't care what the effects are. Normal people don't notice and would rather be disgusted by the grilled rats. The Solarpunks have too little opinion of the Lost. . .
But the general gut feeling is: If you drive out the lost in an area, you will soon have the animals there.
That is why one often unconsciously does not act consistently against the lost.