\chapter{Genesis}

It's the year 2050. The last few decades have been a wild ride. Especially after people realised that they had to deal with several disasters at the same time and that the simplest solution was to rebuild society as a whole, it was: Do it or die trying.

They did it, they survived. Most of them.

Thanks especially to the Solarpunk communities kickstarted by projects like the famous \hyperref[ch:pioneer fund]{Pioneer fund} in the 2020s. The Pioneers started a revolution with extreme out-of-the-box thinking and technological/environmental awareness. In their communities - almost self-contained experimental laboratories - they were experimenters and guinea pigs at the same time. And the general public called Norms watched with curiosity, fascination and hope. The successful experiments where scaled up to industrial scale by the Norms. They integrated these successful approaches into their own lives adapting their cities to match the new reality.
As a result, by 2050 society as a whole is CO2 neutral, fairer, more peaceful and more open.
The Pioneers saved the world - and yet they can't stop being the incubator for epochal upheavals and mistakes.

A third faction got lost on the road to transition - the so called "Dirty road to Eden". The Lost saw the price that had to be paid and disagreed with it on a moral level. Instead of pushing for a new future they looked to the past. Or a mixture of the old ages of humanity. They live in the ruins left by catastrophe and transition. They are collect, recyce and reuse old technology. They became survival experts, fighters and historians.

While the Pioneers and the Norms prefer to forget the recent history. For them some things are better forgotten.