\chapter {Lost detailed}




\section{Profile}
\begin{itemize}
    \item Appearance: Military clothing, body armor, pads. Short hair
    \item Taboos: showing weakness, accepting new things
    \item Architecture: wagon castles, corrugated iron shacks, trailer parks
    \item Resources missing: Diesel and old spare parts
    \item Psychotherapy: Weakness does not exist. This is why therapy doesn't exist
    \item Media: The Lost run pirate channels to broadcast their view of the world (often hatred, half-truths, and misunderstandings of science).
    \item Education: essentials (reading, arithmetic) for 4 classes. No education whatsoever, very little history or culture. Shooting, welding and driving is learning-by-doing once you are considered mature. Anyone can "teach". . .with corresponding results.
    \item Diet: Grilled meat (sometimes roadkill-grilled-on-an-old-oil-drum) and "classic food" from the 1990s. Like hamburgers, fries or hot dogs from the microwave
    \item Names: generals. People from History: Brutus, Hannibal, Ramses, Alexander, . . . Often not so wisely chosen. Brutus, for example, is the son of the prodigal Caesar. . . .

\end{itemize}



\section{The Mystery of the Lost}
No one, including the Lost, is really aware of the important niche the Lost occupy in the ecosystem. Areas where the Lost have been completely driven out are soon overrun by mutated animals.
For the Lost are the Alpha Predators with no exquisite taste in flesh. They hunt the giant bred rats, dogs and cats for consumption. They cook them at the campfire. Add beer and beans.
This keeps the animal population small. The Lost don't care what the effects are. Normal people don't notice and would rather be disgusted by the grilled rats. The Pioneers have too little opinion of the Lost. . .
But the general gut feeling is: If you drive out the lost in an area, you will soon have the animals there.
That is why one often unconsciously does not act consistently against the lost.