\chapter{Story nuggets}

Story nuggets are NPCs, events and locations you can use in any story. In some cases I will add examples how I integrated them into my adventures. But you are free to change that and insert them any way you want.

\section{Jaime and Elisabeth von Walther}
\label{sec:Jaime and Elisabeth}

Jaime and Elisabeth von Walther, Zeppelin for hire

Jaime and Elisabeth von Walther are enthusiastic Zeppelin pilots. And very hospitable.
The Norms work as pilots of a 10-passenger Zeppelin, which is very comfortably equipped inside. It can carry some load in addition to the passengers.
The interior can be quickly rearranged by them (rows of seats, lounge, cinema, luxury bed, ...) and is their home.
Both take turns in the jobs of pilot and steward. Since they both have the same clothing size, they make a joke out of simply swapping clothes and roles in the cockpit between jobs. So each wears the miniskirt at times.
They are quite open as a couple. In the marriage agreement it says:
"Each may go to bed with strangers. But must ask the partner if he/she wants to join in".

These two are a convenient and comfortable shuttle "into action" with possible personal entanglements should they fall for a character or NPC.

They used to work at Dumpit/Cargo (See Albstadt Adventures). When that was closed down by the UN, they cleverly got out. They took the opportunity to buy the little Zeppelin.

\section{Gene Dealer}
\label{sec:Gene Dealer}

The Gene Dealer has set himself the goal of collecting and preserving the genes of as many plant and animal species as possible.
For this reason he is travelling the world.
He doesn't really belong to any of the three factions, but is very welcome everywhere he is known.

Today he is 70 years old and has a scarred face and very poor sleep. And wakes up with nightmares.
Because of his age, the Gene Dealer often has helpers - especially in rough terrain. Their job is to collect samples and seed of plants.

Before the disaster, the Gene Dealer used to discuss the economy and share prices on television. When the climate catastrophe had long been on the horizon. The recommendations to invest in fossil fuels - and thus contribute to the catastrophe - still deprive him of sleep today. In his delusion, he later destroyed his face so as not to be recognised.
Genes are collected as gene scans using portable recorders or simply as seeds. Both are readily exchanged.

\section{The Travelling Eradication Restaurant}
\label{sec:Eradication Restaurant}

Invasive species (plants and animals) can stress local ecosystems. The Travelling Eradication Restaurant is a collaborative project between Lost and Pioneers to hunt and eat these invasive species.
The 10 people who organise it track down the invasive species, move their mobile restaurant to the location and start studying the species to find the best way to hunt them. They build traps and weapons and identify the perfect recipes to match the local food sources.
After sending out an invitation to the nearest Norm Hive, they start hunting and cooking.
Norms love novelty. But most of them do not want to be bothered with the details of eating real animals.
Once the invasive species has been eradicated from this location, the group will move on to new adventures.

\section{Igors Insects}
\label{sec:Igors Insects}

Igor, a Pioneer, is experimenting with insect-based food. His mobile restaurant and automated factory is his home base. Three types of insects can be bred in parallel. When the food order arrives, small portions are cleaned, processed and cooked.
He has a static menu of 20 different dishes. As a Pioneer he is constantly experimenting with new recipes resulting on the "Special of the Week".
Naturally, his meals attract a lot of criticism. This is due to his tendency to add extra cream and cheese even when the combination is particularly odd. Nevertheless: The results are delicious.

\section{Scientific underground}
\label{sec:Scientific Underground}
A small team of scientists spreading knowledge, the scientific method and chaos wherever they go. As a running joke, they never call each other by their real names, instead swapping them every time. One is called by all male names beginning with "R",
The other with "N". The third person in the team is called "Minion". And she is rarely seen. Her job is to clean up the mess the other two have made by spreading knowledge.

\subsection{N*}

\begin{npcBox}[title=N*]

    \begin{aspects}
    \item \aspect[High Concept]{Scientist, explainer}
    \item \aspect[Trouble]{Spreading knowledge even if it causes trouble}
    \item \aspect[Aspect]{A scientific approach to everything}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{4}
        \item \nskill{Athletics}{3}
        \item \nskill{Burglary}{0}
        \item \nskill{Contacts}{3}
        \item \nskill{Crafts}{1}
        \item \nskill{Deceive}{0}
        \item \nskill{Drive}{1}
        \item \nskill{Empathy}{0}
        \item \nskill{Fight}{0}
        \item \nskill{Investigate}{1}
        \item \nskill{Lore}{0}
        \item \nskill{Notice}{1}
        \item \nskill{Physique}{2}
        \item \nskill{Provoke}{0}
        \item \nskill{Rapport}{2}
        \item \nskill{Resources}{0}
        \item \nskill{Shoot}{0}
        \item \nskill{Stealth}{0}
        \item \nskill{Will}{2}
     \end{skills}

    \begin{stunts}
    \item \stunt{Cardio}{Thanks to a scientific approach to training, he gets a +2 to Drive/Atheltics when escaping by bike or on foot.}
    \end{stunts}



    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}
    A friendly, slender, well-trained man with a sharp mind. Ready to fight for science by explaining it. Always thinking of new ways to do it. His latest ideas are small business cards that double as test strips for chemicals and pharmaceuticals. He also runs a pirate radio station.

    If you meet him at a party, he will start drawing diagrams and explaining things on any available surface.

    He approaches everything the scientific way. And with the tools he builds. Sometimes with more success (training and sports), sometimes with less (potted plants).
    Usually seen with a bottle of beer.

    \end{npcDescription}

\end{npcBox}

\subsection{R*}

\begin{npcBox}[title=R*]

    \begin{aspects}
    \item \aspect[High Concept]{Scientist, experimental}
    \item \aspect[Trouble]{Ready to risk something to spread the knowledge}
    \item \aspect[Aspect]{One more experiment I survived.}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{3}
        \item \nskill{Athletics}{0}
        \item \nskill{Burglary}{1}
        \item \nskill{Contacts}{1}
        \item \nskill{Crafts}{4}
        \item \nskill{Deceive}{0}
        \item \nskill{Drive}{0}
        \item \nskill{Empathy}{2}
        \item \nskill{Fight}{1}
        \item \nskill{Investigate}{0}
        \item \nskill{Lore}{0}
        \item \nskill{Notice}{2}
        \item \nskill{Physique}{3}
        \item \nskill{Provoke}{0}
        \item \nskill{Rapport}{1}
        \item \nskill{Resources}{0}
        \item \nskill{Shoot}{0}
        \item \nskill{Stealth}{0}
        \item \nskill{Will}{2}
     \end{skills}

    \begin{stunts}
    \item \stunt{Hardened}{No one knows why. But damage from electrical sources or from cold (like from liquid nitrogen) is always reduced by 2.}
    \end{stunts}

    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}
    Of the two scientists, he is the smaller and heavier one (no sports focus) with lots of tattoos. For non-scientists, he is more approachable and can explain a thing or two with improvised experiments. Some of them will fail, but for unknown reasons he has not been injured yet.
    If you meet him at a party, he will start stacking chairs to explain how a bridge works or something similar.

    Usually seen with a bottle of beer.
    \end{npcDescription}

\end{npcBox}

\subsection{The minion}

The third NPC, "The Minion", is the most ominous. She arrives to save the day when the others have got themselves and possibly the protagonists into deep trouble. She is a cross between a ninja, Mac Gyver and a conman - trying all sorts of tricks to get everyone out of trouble. She usually succeeds, but leaves a trail of chaos that has to be cleaned up later.

As nothing is really known about her, we cannot give you a spec sheet. But her skills seem to be impressive and surprising.