\begin{pioneertalk}[title=Emergency Kit #6]
    \begin{itemize}
        \item \npcquote{Coil, Pioneer}{Lindberg, you copy? I have a problem}
        \item \npcquote{Lindberg, Lost}{Coil, I thought you were visiting your Norm sister. What is it? Over}
        \item \npcquote{Coil, Pioneer}{Can you hurry to my lab and get me Emergency Kit 6? We have a small emergency.}
        \item \npcquote{Lindberg}{I'm already in my truck. Should only take a few minutes. What happened? Over}
        \item \npcquote{Coil}{She said, "In the Hive, we can control the whole city with our Hive controllers, try yours. I can even build a house", I said "I grew my house 3 years ago, it can't be that hard. Why do I have to go through a 2 year tutorial first?", she said, "The app can do so many things. And afterwards it will trigger the Hive AI to coordinate the robots and the crews", I said "I think I can hack it with a simple SQL exploit and skip the stupid tutorial"}.
        \item \npcquote{Lindberg}{Just arrived at your strange pioneer settlement. Over}
        \item \npcquote{Coil}{I said, "Here you go, I am root. Loaded the example and placed it in AR. The green button starts building ?", she said "No ! Stop it! Red button, red button!", I said "Well, my app just crashed, can't reach the server either. Something must have messed it up."}
        \item \npcquote{Coil}{Then these robots appeared and started building what I had designed in the app.}
        \item \npcquote{Lindberg}{Ok, I have Emergency Kit #6. "Robot Uprising". Dynamite, thermite, a hydraulic cutter. Nice. Over}
        \item \npcquote{Coil}{Can you please hurry? A new application started and asked me to finish the selection of furniture.}
    \end{itemize}
\end{pioneertalk}