%% Religion and other complex stuff is stored here
%% It will get an own book

%% TODO review

\section {Gaianism or Weavers}

A new religion is currently being born. And in strange ways it is not replacing any existing religion but extending and refining them. People finding guidance in believing in Gaia - the spirit of the earth and the whole eco systems - often keep their religion and weave it into a consistent world view. As Gaianism is not dogmatic it is flexible enough.
For some Gaianists Gaia exists as a feeling and thinking organism. On the other side there are followers of this religion declaring it is an important metaphor to understand that everything depends on everything else and that's it.

Those extreme sides love to meet, drink some tea and learn from each other. Because even in this young stage of this religion some rules were already established.

For Gaianists the technosphere, ecosphere and sociosphere must be re-balanced. In the past human intervention sometimes intentionally broke this balance. While the technosphere is a part of Gaia the Lemmings forced it into a shap that made it a parasite on the other two parts - ecosphere and sociosphere. While it could be a symbiont.

\subsection{Gaianism rules}

\subsubsection{Tea and respect}

A symbol for this religion is a small woven carpet. As no threat can form a carpet without many others and everything is tied together so are humans, nature, technology. To solve conflicts and create another piece of the fabric Gaianists love to meet others and learn from them. Most Gaianists have their own garden with herbs for teas. Or did a deep dive into the lore of tea making to support their effort.

\subsubsection{Be involved}

No Gaia priest will be a pure Gaia priest. Their place in society is to be a well connected part of it. This is why they tend to have jobs or tasks where they help other people. Very often they change their jobs to benefit from as many perspectives as possible and find new threads and people to weave with.

\subsubsection{Small patterns}

Gaia priests gather followers. But to avoid toxic leadership a Gaia group will split when reaching 23 members. Either a older student will be selected to lead a second group, or another group must be found. In addition it is a bad habit to stay more than 3 years with a single Priest. Or for a Priest not to spend a month every three years as a student of another priest.

Priests become priests because people choose them to be a priest.

Because Gaia followers realized that an inbred community will turn toxic and die.

As a footnote: The Gaia religion is so new that this switching and shifting is declared as a rule and accepted. But did not happen often yet.

\subsubsection{Teaching building bridges}

While Gaia priests build bridges between different groups all the time their main achievement is when they are able to teach others to build a bridge. This is where a group of protagonists can be recruited to build a bridge between to enemies or a group of people and the technosphere or the ecosphere.

The bridge builders will get a small award: A carpet woven by the priest, with symbols depicting the achievement in a symbolic way. This carpet can be small enough to fit into a pocket. This carpet is more than a symbolic gift. By showing it to any other Gaia priest they can proof their deed and get support.

While a Gaia priest may life in a faction or has been born in a faction they try to achieve a state of mind where faction alignment is not relevant any more - being humans this can challenge some more than others. But the goal is to achieve a society state where factions blend into each other whitout losing their identity. But this is a topic still under discussion between followers of Gaia.

\subsubsection{We are just the descendants}

Gaia priests are very aware than many old religions have the elements how to respect nature already in them. This just got out of focus. Be it Eden, Noah saving the animals or nature spirits and shamanism. Some religions even have fractions that focus on nature (Christian Franciscans as an example).

As the Gaianists were born in the catastrophes of the recent years they are aware that they are y engineering their religion and need some foundation to ground it on. Because they to not have a lived tradition and will not have a tradition for the next few hundred years. Other religions are their teachers and siblings.

\subsubsection{Local is Global is Local}

In some areas of the world the Gaia priests are very aware that there have been local traditions, legends, religions or practices that were created by the local community hundreds of years ago. Or grew there naturally. If this local spirituality aligns with the Gaia philosophy you can very well experience a resurrection of those traditions by the Gaia priest.

This will lead to interesting insights and experiences for outsiders visiting and experience a very traditional and specific Gaia worship.

\subsection{Toxic Gaianism}

Gaianism is young and in some situations it already turned toxic. The main cause is that the three systems: ecosphere, sociosphere and technosphere are not equally accepted and respected. Maybe one of them is even declared evil. This can result in a situation that is contrary to the Gaia believe and will turn more and more toxic in this area.

\begin{itemize}
    \item If the ecosphere is declared tge problem you will find restrained nature or no nature at all. With people leading an artificial life
    \item If the sociosphere is declared the problem humans will be displaced and only a few chosen ones will be living there. Picked by some arbitrary marker
    \item If the technosphere is declared the problem humans and nature may be happy for a few years - until some disaster strikes. This can be as simple a thing as a virus spreading and no medical technology is available
\end{itemize}

\subsection{Pilgrims}

This is not an established tradition yet. But Gaia pilgrims show up where Gaia was wounded. And start healing. After the wound was healed the place can become a permanent place for pilgrimage. With a place to stay and learn about the wound and the healers. A place to contemplate, become a better person and learn the skills needed to heal a similar wound.

%% TODO review end


