\chapter{World for the GM}

Many events lead to the world of 2050. And they can all be the source of story arcs. The people of 2050 are only aware of some rumours. But the real events are much more drastic and have a strong impact on 2050.

\section{Billionaires from outer space}
\index{Billionaires from outer space}
\label{sec:Billionaires from outer space}

The world of 2050 is post-capitalist. This is because the billionaires have secretly left the Earth. These are the events leading to the exodus:

\subsection{When money does not help, more money helps}

Billionaires are used to being insulated from the consequences of their actions. With their money, they can buy all the lawyers, managers and scientists they want. And that is why they have botched their money-driven approach to saving the planet. Instead of really understanding science, ecosystems or society, they just took a stupid idea and force multiplied it with their money.

The fallout like giant mutant monster hamsters still exist in 2050. As well as some relic companies that are still going down the road to chaos.

\subsection{Eat the rich festivals}

Having failed, the billionaires tried something new and threw a lot of money at it. Science festivals. Basically music festivals where they celebrated themselves and each other and tried to win followers. These followers had the chance of a lifetime to get a brain implant.
Those who got the implant became true believers in capitalism and followed their new leaders. The implant triggers a serotonin cascade when certain trigger words like "line goes up", "investment" or "shareholder value" are mentioned.

Each billionaire was given a single chance to convince people to follow him. This was the last time that billionaire was seen in public.

What really happened: The billionaire left Earth for his secret base on the far side of the moon, taking some followers with him and leaving some as sleepers on Earth. Some of them watched over their underground lair, filled with technology and tools for their master's return.

The last billionaire to cross the orbit triggered the Kessler Syndrome, making it impossible for anyone to follow.

After a year, all the Billionaires left Earth. People began to wonder what had happened to them. The joke was that all the Billionaires were eaten at these festivals. The term "Eat the Rich Festivals" was coined. In case of an outbreak, the health authorities would freeze small portions of food. These were taken out of the freezer and analysed. The results were never published. Because they found: All the meat served at these festivals as doner kebabs, sausages and the like contained human DNA. Specifically: That of the billionaires.

The truth: These festivals were organised in the early days of lab meat. Some of the billionaires thought it was a joke to clone their own cells into meat and serve it there. They expected chaos when people found out. Animal-based lab meat will become a thing about 2 years later. And nobody thought about the possibility.

The original name of these festivals was "Meet the rich festivals".

\subsection{On the moon}

The billionaires are a territorial group. They do not cooperate well. With the one exception of getting everyone out of Earth's gravity well and into their own moon habitats. There all cooperation has broken down and they keep each other in a state of cold war with a tendency to get hot.

These habitats are depressing little survival bunkers. They are built in a hostile environment (the moon). Where the billionaires live with their brain-implanted Igors and Renfields. They still want to control life on Earth through their remote organisations and agents. Each of them has their own groups and resources on Earth. But the structure is similar.

\subsection{Their minions: The acolytes of the invisible hand}
\label{sec:acolytes of the invisible hand}

This group is a sect of capitalist believers. They are not a secret order - as their level 1 acolytes are actively recruiting new followers.

Unbeknownst to them, they serve the billionaires from outer space.

Acolytes have a coin with their level and the invisible hand marker for recognition. The coin also has RFID features.

\subsubsection{Level 1 acolytes}

Anyone can join in. To get to level 2 you have to deposit the very high amount of 1000€. The structure of a pyramid system is explained to them and they are encouraged to recruit as many others as possible into this system.

\subsubsection{Level 2 acolytes}

You get an app for the Hive controller. It mines cryptocurrency. This partially disables your own controller. But it is possible to recruit other volunteers to help with mining.
The 23 per cent who have deposited the most at the end of the phase go to stage 3. Since it is not transparent to them who has already deposited how much, it is always a risk.

\subsubsection{Level 3 acolytes}

This level is the same as the previous one. Only a new mining application is made available. It is a computer virus that can infect hive controllers. This leads to partially paralysed hives and fights between individual level 3 players for the controlled hive controllers.
As before, the 23 per cent who pay the most will advance to the next level.

\subsubsection{Level 4 acolytes}

At this level you get an application that is compatible with the Hive Core itself. This has much more processing power than individual Hive Controllers.

If they can physically get to this core, they can use it to mine. This makes the total failure of an entire hive catastrophic.
As before, it's survival of the richest, again 23 per cent.

\subsubsection{Level 5 acolytes}

At this stage, they discover that crypto-money is worth nothing outside the invisible hand. There is no scarcity in the world of Norms. They learn at this stage that food, shelter, energy and transport must become scarce products in order to give real value to their money.

They use sabotage, attacks and other creative means to achieve this. Terrorism pure and simple
They become desperate when they realise that crypto-coins are only worth anything to their followers.

\subsubsection{Master of the invisible hand, Level 1}

When they reach this rank, they will receive their Loyalty Brain Implant in a ceremony.

At Master Level 1, they will gain access to some of the hidden resource bunkers that the Billionaires have hidden on Earth - just in case.

These bunkers contain tools to build a new capitalist civilisation on Earth, or tools to help the billionaires return to Earth when the stars are right. Or just a room full of useless dollar bills.

Each year they serve and survive gives them another level. And each level unlocks more of those prepper bunkers and adds more tools to their arsenal, slowly turning them into Bond villain threats.


\subsection{Using this story arc}

The three factions have different approaches to the economy. But hardcore capitalism is not one of them. If you want to explore alternatives to capitalism, get the players used to the different economic approaches. Then add some people who want to turn back the clock to capitalism, while sending the protagonists on quests where they slowly uncover the secret of the billionaire base on the moon.
Maybe this is a secret better shared only with people who can handle it. Or should everything be public?

\begin{itemize}
    \item If anyone were to get the DNA data from the hidden lab, it would cause a scandal.
    \item Reading the full report would create even more mystery: The lab estimates that about 500kg of each billionaire was eaten - impossible!
    \item The real event of billionaires leaving Earth would be a world-shattering one.
    \item The billionaires will continue to pamper their relic companies and try to rebuild capitalism using their underground storehouses and sleeper agents.
\end{itemize}


\subsection{Inspiration}

\begin{itemize}
    \item Iron Sky
    \item Billionaires plan cage match
    \item Glass Onion
    \item Billionaires build submarines and think the laws of physics do not apply to them
    \item https://pluralistic.net/2022/09/13/collapse-porn/#collapse-porn
    \item Bioshock
    \item The book "Survival of the Richest"
\end{itemize}

\subsection{Clues and adventures}

Players will learn about this conspiracy through a ladder of dropped clues. Some of the quests included here already contain some of the clues. It is common for you to drop a clue several times before the players can connect it to the bigger picture.

\subsubsection{"Eat the Rich Festivals" existed}

The Ravensburg adventure, with a film premiere and an old book of laboratory data.

\subsubsection{Something is on the moon}

A radio dish in Albstadt is pointed at the moon.

\subsubsection{The meat was billionair}

In Ravensburg they will find a lab report with DNA analysis. !00 percent of the meat comes from a single billionaire.

\subsubsection{Something is odd}

The Ravensburg report will also say that there is 500kg of Billionair meat. You can guess that it might have been produced by an early in vitro meat laboratory.

\subsubsection{Preparing for space}

In Salem, a gymnasium next to the boarding school for rich children was secretly converted for space training.

The Pyramid to the Stars adventure is about the accidental death of a billionaire who failed to go to the moon.


\section{Religion and spirituality}

\begin{warning}
    Religion is a work in progress. I want to tread carefully as I do not want to hurt people. The rough outline is here for you to use in your group. More details and adventures will be added. With the help of experts for their beliefs. So far I only have access to Catholic theologians.
\end{warning}

Spirituality and religiosity are at the core of human existence. In 2050, people will have many opportunities to seek knowledge beyond the physical world.
However, the catastrophes of the recent past have had similar effects on all religions: All have clearly divided into a light and a dark side.

The dark side is driven by fear and the end of time (as the upheavals are interpreted). People in positions of authority use the teachings to exercise power over other people and restrict their freedom.

The Light Side offers people help and a path to higher realisation. Without coercion. But with more or less clear guidelines, depending on the philosophy. However, people are also encouraged to change philosophy if they come to a point on their path of life and realisation where other help would be important.

\subsection{The dark side}

The Dark Side is easier to embrace. But cooperation is not possible between different factions of the Dark Side. Even within the same faith there can be different Dark Side approaches (sects) competing for the one truth.
The great advantage of the Light Side is that they can cooperate. And without cooperation they will lose to the simpler and more seductive message of the Dark Side.

\subsection{Fighting the dark side}

The UN is asking all religions to fight their own dark side. They are creating groups of spiritual warriors to do this. These groups will either directly fight agents of the Dark Side, or help with rebuilding, community building, pilgrimages, caring for people, or recovering lost religious artefacts.

Knowing the past, the UN has set some rules for these groups:

\begin{itemize}
    \item The leader of the group must be of the same faith as the Dark Side group they are fighting (for reasons of responsibility, "It's your mess, you're gonna clean it up").
    \item Each group must consist of at least three different faiths (and the 45-page letter from a Catholic priest requesting that a Protestant Christian be considered a different faith was answered with "LOL, no").
    \item If it is not a combat mission, external witnesses must be involved to verify that the rules are being applied (this is a job for player characters. Just hope it does not suddenly become a combat mission)
\end{itemize}

Most of the missions these groups have are not combat missions, but things like organising a spiritual retreat or rescuing and rebuilding lost communities.

\subsection{Catholic church}

In the Catholic Church in 2030, there were already strong progressive currents (gay marriage, women priests, ecological free radio and solar power from church roofs) and conservatives (Latin liturgy, preaching away from the people, all climate catastrophes a punishment from God, the end is near). Both are strongly present in the church and a schism might have been the right way to go.

But it got worse.

The change began in 2035, when the new pope boldly called himself "Ratzinger I". Even the election was a bit strange. The Swiss Guard and emergency doctors were called to the conclave several times. But after the election of Pope Ratzinger I, all those involved confirmed that it was all just mistakes. This was the beginning of the Church's dark period and the rise of the Inquisition. The Inquisition scored its greatest coup when it interrogated the murderer of Pope Ratzinger I (the monk Ignazius, who strangled the Pope with a specially made rosary suitable for close combat) and uncovered a large progressive network in the Church and other religions and thinned it out in secret operations (regarding the other religions: the rosary was probably based on the weapons experience of the Shaolin monks. Eyewitness accounts of the assassination of the Pope, for example, also suggest that the murderer had undergone Shaolin training). Unfortunately, Ignazius died during the interrogation.

This orgy of violence by the Inquisition forced many Catholics to choose sides.

The choice of the next pope was simpler. Frederico - a reformer - was quickly appointed pope. He went down in history as Magdalena I, the first transsexual pope. Her reign continues and is very successful. Although she seems to have lost control of the Inquisition. But the Swiss Guard has so far been able to prevent all assassination attempts on the Pope or other church representatives.

The events described here took place over decades. And felt less implausible to many than the election of a reality star as US president in the 2020s.



% TODO \subsection{Clues and adventures}

% TODO \subsubsection{Assassination of Ratzinger I}

% TODO \subsubsection{Introducing the sides}

% TODO \subsubsection{Faith and the new world}


\section{Global south and transhumanism}
\label{sec:Transhumanism}
\label{sec:Global South}
\index{Transhumanism}
\index{Global South}

\begin{warning}
    This is a work in progress. I will need experts to do it properly and respectfully. Especially if I want to make the rules for playable characters from the global south. Players repeating 2 stereotypes all the time would hurt people - especially in a solarpunk setting.
    Please give me feedback! I need different points of view here.
    If you and your group are not comfortable with this idea, just skip it. It is optional.
\end{warning}

No region has been hit harder by climate change than the global South. It reached a level where "people, animals, vegetation and ecology cannot survive". So people had to redesign the ecology and themselves from scratch to adapt to the new, harsh environment.

No one outside the Global South noticed. Because everyone was busy dealing with their own catastrophes, and communication was difficult because all the satellites had been de-orbited by \hyperref[sec: Kessler Syndrome].

The Global South was hit early and hard by climate change. The only thing that saved them was the technology to copy and digitise a person's consciousness and knowledge. Without harming the person. It just creates a digital twin in a virtual environment.
But it can evolve independently. And run overclocked.

Humans were smart enough to only allow wise people to enter this realm. Being smart was a bonus. This forms the virtual elders or ancestors (the nickname for these spirits). People can visit these elders and ask for advice.
And these elders can advance technology by leaps and bounds. This was necessary because the environment was rapidly turning into hell.

As a next step, the plan was to transform humans, vegetation, animals and ecosystems into something that could survive on the new planet. Pioneer technology may look very advanced - and it is. But the level of transhumanist technology can only be described as "alien". To avoid drastic negative effects on society and individuals, the transhumanist plan requires three additional changes:

\subsection{Secrecy}

This whole project must be kept secret from everyone else on the planet. Because it is not the easy shortcut that everyone should take. It comes at a cost, and it is much better that others invest their energy in transforming their society in a less drastic way.

This is why villages and environments look the same on the surface. While the people spend the hard times of the year in underground cities, shelters built with high tech.

This is also the reason why all body modifications are hidden and invisible. And these can be either at the genetic level or through implants.

In some regions of the global south, conditions are tolerable without this transformation. And the lucky ones there just live like all the other factions on Earth: As Lost, Norms or Pioneers. This has the added benefit of providing regions where the few travellers from other continents can be safely accommodated without stumbling upon one of the world's greatest mysteries.

\subsection{Anchoring}

The greatest fear after the forced movement towards transhumanism was the loss of human nature.
That is why everyone who is forced into this path makes an incredible effort to be human. Learning and living their history and traditions. Connecting with people (be it tribe, family or strangers). Connecting with nature, the spiritual world or song.

It is a matter of survival - as a human being.

And it is an even greater gift than the one or two superpowers granted by transformation into a transhuman form.

\subsection{Help}

An essential part of anchoring is offering help to other people. Not helping people in need is one of the fastest ways to degrade your own humanity.

And of course they offer help where they can. People from the Global South travel around the world helping communities bootstrap projects. Pioneer communities are visited to spread technological advances. Norm communities for scaling effects and Lost Communities to guide them to lost treasures of the past. The trick is to do this without breaking their cover story or introducing an implausible technological leap.

There are not many of these agents, as the skills required are very specific. But a group of protagonists travelling around the world might encounter one or two of these catalysts without realising that they are the reason for a fundamental change in that particular place.

But these specific agents are not the best way for the Global South to help others get back on their feet.

The easiest way to help others globally was to put the UN in charge of coordinating global reconstruction. The new UN is not entirely run by the Global South. But these countries have played a big role, supporting it with manpower, tools and experience. The UN is a foundation for rebuilding planet Earth.

\subsection{Head hunting}

Small groups of transhumanists roam the world, headhunting. They are looking for wise game-changers to join their "ancestors". These game changers must first be persuaded to travel to a country in the Global South (with the false image of a disaster area causing problems).
Then they are shown the real situation: A technologically transformed society and environment.

Convinced that the transformation has really taken place, they can participate in a ritual to contact the "ancestors". After days of deep conversation, they may be allowed to join the ancestors by creating a virtual copy of their identity.

Whatever the decision, the Game Changer will return to her homeland. With the sacred promise never to speak of what has happened. Based on the vote of the Ancestors and the decision of the Game Changer, a copy of the Identity will now live with the other Ancestors in the Virtual Realm.


%% Story arc saving history

%% Story arc re-naturation, recycling, wild west

%% Story arc UN

%% Story arc recycle, rebuild, find resources, rescue

