%% A small world description specifically for this adventure.
%% It is compiled in instead of the large variant when the text is compiled as quickstart

\chapter{Small world description}

Some guides for the GM

\section{Pioneers}
\label{sec:Pioneers}
Guide to playing Pioneers: They are always busy with some project or other. They will tell you about it and try to recruit you. Either that, or they will throw the most absurd party ever. This drive can also be destructive, and accidents are quite common in a Pioneer society. But the experience of dealing with laboratory accidents has also grown.
Make it fun and dynamic.
They stretch towards the future like leaves towards the sun.

\section{Lost}
\label{sec:Lost}
Guide to playing Lost: This group is deeply rooted in the past. They distrust high tech (basically anything with a microcontroller). You will find survivalists, militaristic types, farmers and craftsmen. But their treasures are things from the past. Especially books.
First and second contact will be with simple people who have the thick skin and survival instincts to deal with whatever nature throws at them. Stay longer with the Lost and you may meet some of the wise and well-read.


\section{Norms}
\label{sec:Norms}
Guide to playing Norms: Norms live in the present. They are always connected to each other, and cooperative thinking is their typical mode of operation. They are also connected to their hive (in this case a distant city) and the Core AI.
It is quite common for a norm to try to reach a consensus before acting.
Living in a post-scarcity economy, most of them are busy producing art and entertainment. Or soap operas. Living in shelter, it is hard for them to accept a harsh reality.


\section{Resource points}
\label{sec:Resource Points}
In the post scarcity world the resource points are the only thing limited. Those represent damage to the nature like burning fossil fuel or using non-renewable resources. For you as GM: Make it the most valuable resource and use it as a carrot.

\section{UN}
\label{sec:UN}
The UN is fake. Without anyone noticing, the upper management left when the disasters struck. But the highly motivated lower ranks - the ones who get things done - stayed. Simulating the great old organisation while keeping the world safe. Most of the UN of 2050 is based in the global south. One of the major achievements is the resource point system. And the continued effort to coordinate volunteers around the world on rescue missions.