% This file can be used to compile the adventure into a standalone PDF without the sourcebook
\documentclass{book}

\usepackage{../../static/templates/fate_latex_template/fate_solarpunk}
\usepackage{montserrat}
\usepackage{ebgaramond}

% For creating example text
% \usepackage{lipsum}
\usepackage[pdf]{graphviz}

\title{Fate Solarpunk 2050}
\author{Thorsten Sick}

\pagenumbering{arabic}
\begin{document}

\chapter{Introduction}

Solarpunk is a SciFi genre about a utopian future. Solarpunk 2050 is the fate setting where this goal is almost
reached. The protagonists, so-called solar punks, live in natural, technology-friendly and socially progressive
communities. Close to the big cities where the normal go about their daily lives - and alienated from the wild life of
the solarpunks.

In 2050 the world is saved from climate change based environmental catastrophes. This is what the innovative solarpunk
communities have achieved, chasing technologies and social changes at record speed through various prototype stages
and trying them out on themselves.
The 80 percent of the population, the "norms" adopted all the necessary changes from the solarpunks to save the world. But
not more than absolutely necessary - and live in a technological, environmentally friendly utopia.
AIs control cities and society. The AI is optimized to maximize quality of life. And this is how low-change cities are
created. With a lot of media consumption and regulated working hours (25 hours per week) in orderly jobs (which robots
could also take over).
Meanwhile, the Solarpunks have achieved their stated goal. But they don't want to go back to the solarpunk-light world
of cities. And so they experiment, tinker and live on in their ever-changing technological utopias. Guaranteed TÜV free.
In the taster adventure, both the Solarpunk protagonists and a group of norms play an important role.
In addition, there is the fact that raw materials of all kinds are declared to be extremely valuable and there is a deposit
on practically every object - even on the inventory of a coal-fired power plant that was buried in a flood 20 years ago. If
you want to build large projects, you need resource points. And you only get that if you deliver raw materials. These are
rated by material rarity and weight.
The personal resource points allocated annually are sufficient for a normal lifestyle. But since the Solarpunk community
is an "experimental brewery with gene laboratory" it has to be tackled.
Also important are the legacies of a few billionaires who tried to establish carbon capture using genetic engineering at
the beginning of the escalating catastrophes 20 years ago.

\input{adventure_1.tex}

\end{document}