%% This is a template for default adventures

\chapter{To the moon}
\label{ch:To the moon}

\section{Topic}

The main theme in Überlingen may be a red pill/blue pill story. Know the truth or take the easy way out and live in a comfortable lie?

With the arrival of the Master, capitalism is threatening the solarpunk biomes the protagonists have encountered in previous adventures. Will the protagonists succeed in protecting the utopia?

\section{Summary}

In pursuit of the billionaires, the protagonists arrive in Überlingen. They encounter a strange esoteric culture. Here they will have to decide how to deal with facts, freedom and the fate of the people.
One step closer to the billionaire's hideout, they meet the pioneer community that fled Weingarten: Waterworld.

Here they will find the body of an Acolyte of the Invisible Hand who was searching for the hideout - killed by pirates on Lake Constance.

Hired by the Master Acolyte, the Pioneers must build a submarine themselves (perhaps with the help of the Sea Witch).

Deep beneath the surface of Lake Constance, the Billionaires have built a bunker. Occupied by Nestor - a loyal servant of his master.

The master himself is on the moon. He is waiting for an acolyte to find the bunker. A videoconference allows the protagonists to speak directly to one of the villains - for the first time.

They can gain access to one of the bunker's locked safes - which contains enough tools to capitalismform the Earth and make it ready for the Billionaires' return.

You will also learn that this is just one of hundreds of hidden bunkers the Billionaires have left for their servants. This is the best time to contact the UN, go on red alert and be ready to receive your next assignment from the UN:

Gather as many Norms, Pioneers and Lost as possible. Prepare them to face the Billionaires when they return. But without telling them the truth - because that would not be credible.

\section{What really happened}

The billionaires went to the moon. All of them. They left behind hundreds of secret bunkers. With all the tools needed to build capitalism on Earth. The protagonist will find one at the end of the adventure. And will have the power to end Solarpunk.
Or help the UN prepare everyone to fight what will be the counter-revolution. Which will start as soon as an Acolyte of the Invisible Hand controls one of these bunkers.

To reach the bunker, the protagonists will explore the surroundings of Überlingen:
\begin{itemize}
    \item {Überlingen, the esoteric town on the shores of Lake Constance. Miracles happen here!}
    \item {Waterworld. The refuge of the \hyperref[subsec:Weingarten]{Weingarten} Pioneers}
    \item {The two Swiss pirate fleets}
    \item {An underwater bunker ready to take over the planet}
\end{itemize}


\section{Überlingen (green zone where it starts)}

The AI uses technology, science and applied stage magic to perform miracles. The esoteric Norm inhabitants are fooled - and happy.

\subsection{Astrological signs}

On arrival, everyone with a Hive Controller will be asked for their birthday.

As a game mechanic: Have the players roll a die to determine their \href{https://en.wikipedia.org/wiki/Astrological_sign}{astrological sign}. This will now be displayed, along with the character's name, above the character's head for anyone using a Hive Controller.
All Überlingen residents and the AI will treat the personal traits associated with the sign as absolute truth. "Of course you are angry. You are Scorpio". This is funny when it fits the way the character is designed - or when it clashes with it.

\begin{tabularx}{\linewidth}{ccccc}
    \hline
    Rolled & Sign & Gemstone & positive char & negative char \\ [0.5ex]
    \hline
    1 & Ram & Red Jasper & Courageous & Self-centred   \\
    2 & Bull & Amber & Loyal & Stubborn   \\
    3 & Twins & Pyrite & Curious & Superficial  \\
    4 & Crab & Rutile & Sensitive & Anxious  \\
    5 & Lion & Citrine & Righteous & Proud  \\
    6 & Maiden & Lizardite & Reliable & Petty  \\
    7 & Scales & Jade & Just & Depressive  \\
    8 & Scorpion & Turquoise & Determined & Authoritarian  \\
    9 & Archer & Chalcedony & Optimistic & Overconfident  \\
    10 & Goat & Rock crystal & Ambitious & Gluttonous  \\
    11 & Water-bearer & Aquamarine & Honest & Vain  \\
    12 & Fish & Rose Quartz & Patient & Lazy  \\
\end{tabularx}

\subsection{Birds aren't real - if it flies, it spies !}

To gather more information, the AI measures samples from the toilet and spies on people using \href{https://en.wikipedia.org/wiki/Birds_Aren%27t_Real}{artificial birds} - Google it for great posters and handouts!
This way the AI knows everything about the health and secret desires of everyone in Überlingen.

When spending time in Überlingen, Lost characters in particular will find the birds "strange" without really knowing why.

The most common birds are seagulls, followed by crows.

\subsection{Working miracles}

There are many esoteric practices and rituals in the population. Some are automated and built into the city. For example: The water taps have a revolver-style device with 12 transparent pipes containing all twelve gems. When someone fetches tap water, the hive controller automatically rotates the correct tube into place so that the water can be energised by the correct crystal.
The real magic, of course, is the medicine that is secretly added to the water - optimised for the person consuming it. This could be caffeine, painkillers, the daily dose of the medication they need to treat their illness, ...

It works!

Of course, you can also order "Full Moon Beer" at Ceres (brewed by the automated Ceres system during the full moon). And spring flower tea (adapted to your personal aura). There is always an Ayurvedic food option - and the Hive Controller will help you choose the right dish.

This is the only Ceres in Germany where you can order yak milk (whoever got the yak cells for the bio-tank is still a mystery). But a few drops in your tea will put your chakras in order.

The AI will generate daily horoscopes for people. And like a miracle, they will come true - AI's stage magic at work.

\subsection{People in Überlingen}

The people of Überlingen are friendly and visitors will be invited to parties in their homes or on the shores of the lake. They will have a great time. But you will have to get used to the way things are done here. At least everything is very mindful, they can try out the sound bowl collection, take a trip to energy places where leylines cross, smoke some weed.

\subsection{Scientific underground}

There is a small group of activists who want to spread the truth by teaching the scientific method. And unveil the mischiefs of the AI. They call themselves \hyperref[sec:Scientific Underground]{Scientific Underground}.


The AI knows them and accepts them - as long as they keep a low profile. They can identify the doubters and make them move to another Hive. Improving the happiness score.
Still, they never stop handing out flyers, holding little science sessions with the esoteric crowd, and pointing out that the birds are behaving strangely. Not many here in Überlingen take them seriously.

\section{Pirates}

Two groups of pirates are threatening the Lake Constance region. Both appear to be based in Switzerland. And both speak the Swiss dialect. But they have different philosophies and are enemies.

\subsection{Rakham}

He is a show pirate, inspired by Captain Jack Sparrow. His wooden ship sometimes "visits" Überlingen and other towns, where he and his crew rob the people. When his black flag is seen approaching Überlingen, people gather on the beach. Finally, a good show. And the few items you lose to the pirate can be replaced by the AI.

\subsection{Blackbeard}

He has converted the old ferries and katamarans to look like vehicles from a Mad Max movie. His fleet is feared on Lake Constance and he is a threat. Of course, he disdains Rakham and his crew. His current goal is to find out what the treasure is that the Acolythes are looking for.

\section{Waterworld}

Waterwold is a floating city built by the Pioneers of Weingarten. It is a collection of bouncy castle style floats in all the colours of the rainbow. Some of incredible size. Transport between them is by boat. Nobody checked the film history when they name it like that. But so far all is well.

The Pioneers here concentrate on research into aquatic life, ship technology and the construction of floating things like buildings and platforms. Some of these floats are used as gardens.

Every night there is a party to show off the latest engineering tricks and research results. This time it is a new supercavitation experiment. After that (and when everyone is drunk) there is a round of tattoo-secret Santa (all the players and the GM draw tattoos on post-its. They are shuffled and the characters get a tattoo upgrade based on what the players drew.)

Waterworld keeps the pirates away with water cannons.

\subsection{Sea witch}

A special character in Waterworld is the mysterious Sea Witch. She lives in her floating tower with creepy decorations. As a counterbalance to the tower above the floating plastic island, there is a 3-storey basement below the surface of the lake.

Visitors must follow a ritual protocol to announce themselves. She herself follows many ritualistic steps that no one can decipher. But she is a genius - most likely someone the protagonists will need.
The truth behind her behaviour: She is neuro-divergent. No one has properly diagnosed all her special ways of thinking and the reasons for them. But the Pioneers found out that she needs structure, and surprises can take her out of the game for days.
Without conscious decisions, these little strange rituals developed between her and the rest of the Pioneers. Everyone is proud to have a sea witch, and by following the rituals they build a healthy structure of mystery.

Their little secret project is to build robot birds for the Überlingen AI. The AI started ordering them a few years ago. The Sea Witch does not care what they are used for, but she loves the challenge. If the protagonists find out about this secret, they can have 1-2 birds that they can remotely control as surveillance drones.

\subsection{Submarine}

The Pioneers experiment with everything that swims or dives - what they lack is a working submarine. But with the help of the protagonists, they can build one. If you want to get your nerd on, have a look at \href{https://media.ccc.de/v/37c3-11828-how_to_build_a_submarine_and_survive}{How to build a submarine and survive} (there is an English audio track in the options).

To build a submarine, you first need a hull strong enough to withstand the pressure of the water. \hyperref[subsec:Friedrichshafen]{Friedrichshafen} as an industrial city might have some. Perhaps an opportunity to visit another town on Lake Constance and add a little adventure?

\subsection{The body}

torture. The pirates found the Acoylte of the Invisible Hand, level 3, searching for something - the secret bunker. But they thought it was a simple treasure. So they tortured and killed him. The Hive Controller was lost in the lake. The protagonists can find it floating there. They may use it to call the Master, or the Master will come looking for it soon anyway.
The dead Acolyte can be identified by the coin in his pocket. But as the Acolyte is not a Master - and has no brain implant - he could not have opened the bunker.

\subsection{The master}

The dead Acolythe was sent by the Master to look for signs of the bunker. A few hours after the body is found, the Master is rowed from Überlingen to Waterworld. He paid 4 people to row for him. He will meet the protagonists, investigate the death of his servant and, after learning that he has failed to find the bunker, pay the protagonists (in Euros) to go and look for the bunker.
This will most likely lead to ....emotional reactions from the protagonists. But when they learn what they are being asked to look for, they will accept - more out of curiosity and to prevent any damage the Master might do, than for the almost worthless money (as we are living in a post scarcity world).

\section{The bunker}

Knowing the area in which the dead Acolyth searched, and having built a submarine with the Pioneers, the protagonists can begin their search. 100m below the surface, they find a concrete bunker with the number "503".
The underwater lock can only be opened by the Master and his implant. So after finding it, the protagonists will have to shuttle him down there.

Once opened, they will find a luxurious apartment. Marble, gold, potted plants and elephant heads on the wall. The worst James Bond villain bunker imaginable. They are greeted by the old butler, Nestor, who has spent the last 20 years locked in this bunker to keep it ready. Now that the guests are here, Nestor hopes his shares will be paid out by the CEO (billionaire) he serves. But should he return to the surface, he will soon learn that there is no longer any market...
Thanks to his personal brain implant, he is still always happy and gets an endorphine rush when discussing capitalism and financial theory.

There is a meeting room where the Acolythe, and most likely the protagonist, can now have a video audience with the CEO. All he has to do is launch the buoy with the satellite dish to contact the moon base.

As soon as the video call works: The old CEO appears on the screen. Behind him, a techno-utopia - and through a window, the lunar surface. Whenever the CEO moves, you can see that this is a video background and that the reality up there seems to be a technological desaster.

He will ask his minions how things are on Earth - the Acolythe will answer as the CEO expects: A shattered humanity. Small islands of something called civilisation. Culture is on the Marxist spectrum. But his Acolythes are ready and well organised to take control (here he lies). The sub-groups of Marxists he has identified are:

\begin{itemize}
    \item {Norms: High-tech and dependent on AI. But for those he already is armed with computer viruses. Soft targets}
    \item {Pioneers: Innovative on a technical level. But not ready for business and can be exploited. He would simply bait them with resources for their experiments. }
    \item Lost: A violent bunch of people, no culture but weapons. Low tech. Tribal. Maybe we just wait for them to die - shouldn't be more than a few years.}
\end{itemize}

The CEO will then open one of the vaults (there are three) by remote control and the Nestor will give the contents to the Acolyte (who will then pay his employees, the protagonists, to carry the valuables to the submarine).

This vault contains everything the Acolythes need to conquer the Earth for the CEO.

\begin{itemize}
    \item {2 Euro pallets of cash}
    \item {3 euro pallets of guns, ammunition and weapons}
    \item {Leather shoes and business suits}
    \item {A map of fossil resources and plans how to extract them}
\end{itemize}

The last point is the world-destroying weapon. If people start to rely on fossil resources - not monitored by the UN - it could be the end of civilisation.

It is not up to the protagonists. If they simply leave in the submarine, leaving Nestor and the Acolyte Master trapped in the bunker (preferably with the antenna cut off), this is an option.
And not a bad one for Nestor and the Master - both enjoy the large library of financial books and discussing financial theories. Their brain implants release small amounts of dopamine every time they scratch a new capitalist topic.

\section{Calling the UN}

The wisest next step is to inform the UN about this bunker - and the hundreds of others yet to be found. It will be difficult to get a connection to Africa - no satellites - but the UN ambassador will be shocked and ask the protagonists for help.

Since it will not be possible to find all the bunkers, the societies will have to be made resistant to the attack. Preferably without telling them about the threat itself. No one will believe them. Lost, Norm and Pioneer Societies must be strengthened. Networks must be built between them. And a first project will be to travel south and build a radio relay station between the UN in Africa and every society they find.

You should also try to find the mysterious Alexandria that the Lost have built.

This will lead to a quest of loosely connected missions. The goal is to befriend and help as many Lost, Norm and Pioneer communities as possible. To have access to their support when the CEOs make their next move.

These adventures can be linked in a "collect the coupon" style. Where the protagonists can choose any adventure from a list of options. And as a reward, they can collect gratitude. Or old books they can trade in for a ticket to Alexandria - once the group has enough books that interest the Lost, they are invited to Alexandria.

\section{Green zone (end)}

The protagonists can spend a few days at Waterworld or Überlingen. Meet the friends they have made.


