\chapter{The Name of the Rose}
\label{ch:the name of the rose}

This adventure is less detailed and is aimed at the game master and players with Solarpunk 2050 world knowledge. It is better suited for improvisation.

It is best played after "Project Lifeguard" where the characters made friends in \hyperref[ch:project lifeguard]{Albstadt}. Even if the characters changed the players could be witness to the results of their endeavour.

\hyperref[subsec:Ravensburg]{Ravensburg} is special. During the night power in this town is switched off. Without power the Hive AI will go offline. Please read the Ravensburg article for more details as they will affect the adventure.

\hyperref[subsec:Weingarten]{Weingarten}, the neighbouring town, is an 80s theme park with a mystery surrounding the missing Pioneer labs.

\section{Topic}

This adventure and the "Eat the rich festival" focus on capitalism and the alternatives to it.
\begin{itemize}
    \item Representatives of capitalism are the billionaires and the acolytes of the invisible hand.
    \item The Lost rely on barter transactions.
    \item The Norms are representatives of basic income with premium products.
    \item Pioneers are a meritocracy.
\end{itemize}

\section{Summary}

A Norm library club in \hyperref[subsec:Ravensburg]{Ravensburg} got a print of the original edition of the book "The Name of the Rose". They want to sell it to a group of Lost for a fair price (5 books).
At the same time a Norm movie, the 25 Episode of the "Eat the Rich Festival" series has premiere. Attracting the Norms to Ravensburg. Those two are connected.
The book is a palimpsest. Someone printed the "Name of the Rose" on the back of some printer paper containing diagnostic reports from the real "Eat the Rich Festivals" which happened 15 years ago. And according to these DNA data the modern myth repeated in the films is true !
While the protagonists try to get all three parts of the book and want to watch the movie and enjoy the after-show party another group is unveiled. The "Acolytes of the Invisible Hand" try to get the book and sell it back for cash.


\section{Getting started}

\subsection{Norms}
There is to be a new episode of "Eat the Rich festival". Episode 25, "Billionair Jambalaya". This will be streamed simultaneously on AR. But it will also be shown live in selected cinemas as a premium offer. With an atmospheric festival as the backdrop !
The Norms want premium tickets. But they are sold out in the current city. It is indicated that there are still many seats available in Ravensburg. So the idea is to travel there, register temporarily at this hive and then go in there with friends (the other characters).
This is the reason for Norms to travel to Ravensburg.

If \hyperref[sec:Jaime and Elisabeth]{Jaime and Elisabeth} became friends and they were helped in Albstadt, they might have organised that as a thank you.

\subsection{Lost}

There is a festive mood among the Lost (Lara from the Albstadt adventure is possibly to be accepted into the tribe). There will be a big ceremony. The player characters are invited. Then news arrives that a book is for sale in Ravensburg: the original of the "Name of the Rose". This is not yet in Alexandria (Lost will know what this means, everyone else will not).
In exchange for the book, the Ravensburg Norm Book Club only wants 5 reprints of other books.
They have often done business with them and are friendly with each other.
The characters are sent off.

\subsection{Pioneers}

Someone at the Pioneers has compiled a list of Pioneer labs. The laboratory in Weingarten (near Ravensburg) has not been heard of for a long time. Pioneer characters are given the task of investigating.

\section{In Ravensburg and Weingarten}

The characters are free to investigate. These sections are not in chronological order.

\subsection{Pioneer mystery in Weingarten}

The Pioneers have left Weingarten because of constant hostility. They used to be in the old high school. But there is now a tidy meadow. The entire university was recycled by them in a very short time. Now there is a meadow.
There is a pillar with a riddle on it. It points to the Pioneers' retreat.

On the column there are markings with strips and two plugs into which you could plug an electrical device. One plaque reads:

\begin{itemize}
    \item Brown, Brown, Brown, Brown, = 110
    \item Brown, Red, Orange, Green = 12 000
    \item Purple, Green, Green = <here is the slot>.
\end{itemize}

These are markings like you would find on electrical resistors. If you understand this and tinker and connect the correct resistor, a hatch opens for you. The correct resistor is 7.5 M Ohm.
(Note for the game master: There are apps that the players can use to calculate the resistance).

There are gears behind the hatch. One is missing.
You have to measure the missing gear wheel, plan it using CAD and print it out with a 3D printer. After inserting it, the mechanism turns. And a fountain rises out of the meadow.

The fountain consists of a dolphin statue and a basin.
The dolphin spits water into the basin. The basin is shaped like Lake Constance. The water enters the lake at about the town of Überlingen.
That's where the Pioneers fled from the people in Weingarten. And founded Waterworld.
In Weingarten, you can find rumours among people about a quick departure. And a lot of resentment towards the Pioneers.

\subsection{Ravensburg, Hunt for the Book}

The Ravensburg book group is very open and happy for a 1:5 swap. The book is divided into 3 folders. At first glance, they are copied sheets with the Italian book "The Name of the Rose" on the front. But on the back the characters can find formulas, tables and evaluations. Many years ago, someone recycled a misprint at his workplace to print out "The Name of the Rose".

After getting to know each other for the first time, problems begin. The book is divided between three people, because they all want to finish their part quickly. Alexandra, Bob and Daniel
Alexandra has written an ominous suicide note and has probably taken her own life - which doesn't bother anyone. If you ask, she often makes such macabre gags around her birthday to then celebrate in her flat. If you don't ask, you get a surprise with a lively Alexandra, should you search the flat.
The suicide note is written in Lovecraft style. "I have read the book and understood its terrible contents. Now my world is destroyed and all I can do is take my own life....but before I do I will leave you with what terrible realisations took my mind. Come to my flat at 22:00 at night".
Alexandra and a cake are waiting there. You can get the book by asking nicely.

Bob has a parkour hobby in addition to his books.  He wants to take part in a race over the roofs of Ravensburg. Afterwards, he quickly finishes reading the book and hands it over. It is quite possible that player characters will also want to take part in this nocturnal race. All they have to do is complete the training course to prove that they are safe.
In the meantime, the acolytes have learned from Daniel that the book fragments could be worth something and one of their number will make an attempt on Bob's life. Bob falls from the roof and dies. Afterwards, Bob's flat is searched for the book.
Here the protagonists can confront one of the acolytes. If they do not succeed, they are offered the book for a high price.

At night, Ravensburg's AI is switched off and can neither prevent the murder nor investigate.

(in a test round they caught the murderer and thief in the flat. A fight broke out and the murderer broke the nose of one of the characters with the book "Das Kapital" by Marx).

Daniel feels like the custodian of the books.  But he is also the first to be recruited by the invisible hand. Now he is one of theirs and in the first rank. He still needs €800 to move up. For this price he wants to sell the book. Because he has blabbed, the others have become aware of the valuable books and also want to earn money. This leads to the murder of Bob.


\subsection{The Name of the Rose}

The original is a very good book (if you know Italian). But the back cover contains explosives.
This is divided into 3 parts and the game master can decide which information the players get and in which order, depending on the suspense.
To read the laboratory analyses, it may be necessary to have knowledge of biology or genetics.

These are laboratory analyses of meat found at the "Eat the Rich" festival at Lake Constance, in the year 2035. This festival had to be cancelled due to bad weather. Much of the data could only be collected because there was still a lot of the food left:

\begin{itemize}
    \item The meat contained human flesh
    \item A billionaire could be genetically identified, the name was anonymised
    \item 500 kg of meat were found from this billionaire.
    \item Laboratory meat production did not come on the market until 2 years later (but the billionaire already had it running in the experimental stage and the few hundred kilos were feasible. The meat is cloned meat on a billionaire basis).
    \item At the Eat the Rich Festivals (Which were called "Meet the rich Festivals") the Billionaires gave a speech. Before they disappeared. Their disciples were promised that after a test they would be allowed to join the future. No one knows: they were implanted with a chip in their brains. Many of the disciples disappeared afterwards (info: they left for the moon with the billionaires).
    \item An address in the document refers to Salem, in the boarding school there a child of the billionaire is at school (forwarding to the next adventure!).
\end{itemize}


\subsection{Tastes like chicken}

As soon as the suspense is right, the premiere of the film will start in Ravensburg. A replica of the festival around the cinema provides atmosphere. Sausage stands advertise "Tastes like chicken !" And indeed: it is chicken from the retort.
In the film itself, the festival is shown (with Hollywood accuracy):
\begin{itemize}
    \item A group of young people are partying at the festival. Many are interested in the music. Only some want to see the billionaires and their promises
    \item Speeches of the billionaires about technological dreams
    \item A Teeny Love story
    \item The horror drama when one of the billionaires has an accident and is unceremoniously turned into kebab. But you've seen that in all the episodes before in different variations. It's more gentle horror.
    \item The nerd has to make a decision: Follow his just-found girlfriend or join the billionaires's company for which he has just been recruited.
\end{itemize}
Since the premiere is sold as a norm-premium product, it costs real euros (as AR it would be free). But the supporting event is fabulous.

\subsection{Acolytes of the invisible Hand}

The trouble is caused by the \hyperref[sec:acolytes of the invisible hand]{Acolytes of the invisible hand}, who operate openly - as they are all level 1 - and need to recruit new people into their Ponzi scheme. At the same time, a member of the book club has joined them and wants to use his part of the book to make money. Others in the group also want to make money and murder another member of the book club and search his house for the book.
