\chapter{Dead Zone}
\label{ch:dead zone}

\section{Topic}

The idea is to experience an AI controlled town with a local culture maintained by AI algorithms and grown by like minded people moving there. This town is the perfect setting for a murder mistery.
The town Ravensburg started to transform when it switched off the public Wifi during the night in the year 2023. People who claim to suffer from "Electromagnetic hypersensitivity" convinced the local government to do that. After the change the slept better.
This was the start of the transformation of the town that became a Norm town int he next few decades. In the year 2050 the situation is: During the day it is a fully automated Norm town with electric public transport and AI support for oyur Hive controller. During the night everything electric is switched off.
"Electromagnetic hypersensitivity" is still no proven fact. But those people still claim to sleep much better now. The reason could be that after 8 pm there is no distraction anymore, lights are switched off and the town turns silent until 6 am.
Starting 2040 more "Electromagnetic hypersensitiv" people moved to Ravensburg. Further shifting the AI algorithm that is optimized for inhabitant wellbeing towards those nightly blackouts.

As the AI is not monitoring anything the night is the perfect time for crime.
The town is also very attractive for different types of adventurers:

\begin{itemize}
    \item Norms can be sent from other Hive towns to investigate why the log feeds coming from Ravensburg peak with alerts at 7:59 pm and crash to 0 at 8:00 pm
    \item Pioneers can be sent to find new solutions to bring a non-electric technology to Ravensburg to fill the nightly gap
    \item Lost will find a town that is not functional duiring nighttime (everyone retrats to the own appartment, best case: visiting friends for candlelight-and-wine evenings) and maybe help them with the side effects of the blackout
\end{itemize}

%% https://www.golem.de/news/elektrosensibilitaet-wangen-und-ravensburg-schalten-nachts-oeffentliches-wlan-ab-2304-173252.html

The topics adventure is "A radical measure that does not solve the problem. But will have positive and negative side effects and maybe even somehow fix the real issue (sleeping better) by accident" and "self re-inforcing cycles".

%% There is a rebel group secretly running wifi (with hidden SSID) and with the skills to switch off power LEDs on electronic devices.


\subsection{Ravensburg}

* Ravensburg suffered from a famine. This is why it has twice the Ceres capacity it needs, a canning factory and storage. The storage is FIFO. All stored goods with a best before lower than one year are sent to someone in need. This can start adventures.
* One of those Ceres is running 24h and is outside the city limits in a secured zone (electromagnetic waves !). The other one, just growing plants, is shut down during the night. Obviously in the second one they can only grow stuff that survives without energy.
* At night they are playing board games with friends, read (candles), go to be early
\subsection{Weingarten}

* 1980 re-enactment. They call it simulation, it is a theme park
* Not sustainable, secretly supported with almost everything
* Tech is forbidden
* They ask for resource points being donated
* First they wanted to make it a Norm town. This is where they built the underground tunnel network to distribute goods to the shops. Robot cars were planned to do the delivery. Now people are moving them in carts. (This is important to hide the needed influx of external resources and create the theme park athmosphere)

\section


%% Start: Ein Lost Spieler wird nach RV geschickt, um von einem Buchsammler ein seltenes Buch zu kaufen. Der will in Euro bezahlt werden, was dann wieder zu Problemen führt. Der Buchsammler ist den Lost bekannt und ein guter Partner
%% Der Buchsammler hat ein Sortiment gesammelt aus: Alten Büchern aus der lokalen Bib, Fundbüchern (er gibt Suchaufträge) und welchen, die er mit Lost getauscht hat
%% Die getauschten hat er den Lost für Naturalien abgekauft. Praktischerweise bekommt er diese ja kostenlos. Er hat sie also genau genommen betrogen
%5 Die Lost verkaufen dem Bibliothekar Bücher, die sie als Nachdrucke von Alexandria erhalten haben mit dem Auftrag, die zu verteilen. Damit haben sie ihn genau genommen auch betrogen
%% Der Bibliothekar stellt viele seiner Bücher in RV zur Verfügung. Wegen den nächtlichen Sperren lesen überraschend viele Norms Bücher
%% Im Umfeld des Bibliothekars finden Morde statt. Es geht um ein Beweis für das Stattfinden der "at the Rich Festivals". Genetische Untersuchungen des Essens dort. (Name der Rose checken !)
%% Man könnte meinen, der Bibliothekar selbst ist in Gefahr
%% Tatsächlich führt er die Morde durch. Er muss verhindern, dass die Leute davon erfahren, dass die Verschwörungsmythen um die Festivals wahr sind. Sonst bricht deren Weltbild von einem friedlichen Umbruch in die Solarpunk welt zusammen
%% wenn die Spiele das verbotene Wissen haben, müssen sie selber schauen, was sie damit anfangen. Das tiefere Geheimnis: Die Reichen haben ihr eigenes Fleisch geklont und sind heimlich zum Mond aufgebrochen. Haben danach das Kessler Syndrom ausgelöst.
%% Sie werden wiederkommen und den Kapitalismus zurück bringen. Wenn die Gesellschaft bis dahin nicht stabil ist.
%% Leute spielen Brettspiele und lesen nachts Bücher bei Kerze