\chapter{The Mystery Club}
\label{ch:mystery club}

TODO:
- Show AR interface
- Explain AI
- Ride through the city (free ride, free breakfast, optional premium barista)
- Explain monetary system: \hyperref[sec:basic incomes]{Basic income} Free stuff everywhere. Except: Premium stuff to motivate people (paid in money) and products that does need non-renewable resources (paid in resource points).
- Enter WEC rocket factory
- Do the normal job
- Afterwards: Meeting at the factory organized club
- Sad time at the team: A co-worker and mystery club member died. Job was end-control of explosive bolts
- Happy time, next day: The bolts for the 100th rocket to the Moon base (which is fully automated) are packed ! Live feed ! But you can see the dead co-worker packing them....
- Mystery club springs into action. And will find several odd things:

Mysteries
- The manual labor in this company is bullshit. To keep people entertained. Robots are doing the real work. But the people are happy....
- The rocket does not only transport machines. But also protein bars. Is there anyone on the moon ? (Yes, the rich people who fled earth) - Finding that is optional and will be a hook for a adventure later
- Some affairs and other secrets
- Characters: All characters are members of the "WEC Rocket Factory Mystery Club". Quite likely everyone works there (external people could still be members of this club, it is not exclusive). There is a bunch of example characters.

\section{Topics}

A well organised ecological society where false self esteem is artificially produced by bullshit jobs. And real one can be found in clubs sharing a hobby with friends.

Where there is plenty of everything available for free. But there still is a simulated scarcity so people can differentiate by spending their money on premium products.



\section{Summary}

\section{Getting Started}

\section{First AR experience}

The Norm protagonists have been using AR for most of their life. But the players must get used to the most powerful tool.

With a gesture they can start an AR assistant that is displayed right in front of them. Depending on the Apps and permissions you have you can control large parts of society, order things, broadcast news, research, ...

To be able to use an App you will have to do the App specific tutorial first. This can take time and so no one has all the Apps available.

If you order an item you will have to pay if it is a premium item or requires non-renewable resources.

After the command is sent to the App, the AI of the city will orchestrate all the people involved in producing the item or service and deliver it as fast as possible.

\section{Ride to work}

\section{At work}

\section{A sad evening}

\section{Next day: Celebration and a mystery}

\section{The open investigation starts}

\section{Moral decisions}

Is it wise to tell everyone that their jobs are meaningless and destroy their source of pride and self esteem ?
