% This file can be used to compile the adventure into a stand alone PDF without the sourcebook
\documentclass{book}

% Encode fonts, fixing Umlaut copy and paste problems and more
\usepackage[T1]{fontenc}

\usepackage{../../static/templates/fate_latex_template/fate_solarpunk}
\usepackage{montserrat}
\usepackage{ebgaramond}
\usepackage{hyperref}

%... other code

% \section{Hello World}
% \label{sec:hello}



% For creating example text
% \usepackage{lipsum}

\title{Fate Solarpunk 2050 - Adventure "The mystery club"}
\author{Thorsten Sick}

\pagenumbering{arabic}
\begin{document}

\chapter{Introduction}

% \hyperref[sec:hello]{Word of text}

Solarpunk is a utopian Science Fiction genre. \textbf{Solarpunk 2050} is the Fate setting where this goal is almost reached. The protagonists, so-called Norms, live in upgraded eco friendly cities: The old houses (built 2020 and before) are hidden behind trees, solar panels roofed bike lanes, and parks. Basic needs are for free. If you want premium products you pay with the Euro (or other local currency) you earn in your 25h per week job. Most things are automated and you can control the automated city and the AI with your Augmented Reality device by interacting witht he virtual interface in front of your eyes.

The protagonists are part of the "mystery club" founded at the rocket center company of their home town - where the play Exits games, create riddles and brain teasters as a hobby. Now they will have to face one or more real world mysteries.

This adventure is part of the Solarpunk 2050 setting but contains everything to start playing. It is based on "Fate Condensed".

\input{adventure.tex}

\end{document}