%% This is a template for default adventures

\chapter{Pyramid}
\label{ch:adventure pyramid}

At the end of this story, players will decide the mental, spiritual and physical fate of Yussuf, Farouk and the duped faithful - or leave it to a dead billionaire.

This adventure will add an Indiana Jones flavour to the game.

\section{Topic}

The Pioneers, from three different factions with different philosophies, come across an isolated group of people with their own religion who need to be saved. For some unknown reason, they have built a pyramid near Berlin to praise their god: The New Ra.

The big questions to be answered during the game are:

\begin{itemize}
    \item Whose body can you save ?
    \item Whose soul can be saved?
    \item Is the price of shattering someone's worldview too high?
\end{itemize}

\section{What really happened}

This story takes place near Berlin, in the Zehdenick/Gransee area. With some minor adjustments you can place it somewhere else.

Perhaps 20 or 30 years ago an unknown billionaire died in a car crash. His will stated that he wanted a pyramid to be built on the site of his death. Including a temple, a temple area, some believers and his own religion praising the "New Ra". Perhaps the drugs he took while writing it were involved.

Of course a pyramid needs traps.

This was all put into a contract and everyone hired had to follow it to the letter. Everyone agreed that the money would be better spent helping people, not building pyramids. And nobody liked the billionaire (they just needed his money) - the people involved used every freedom in the contract to sabotage the plan.

\begin{itemize}
    \item The high priest Farouk forgot the billionaire's name and erased it from the cartouches of all the obelisks.
    \item The engineers who built the traps were used to safety engineering. The traps are as safe as possible.
\end{itemize}

Farouk created the religion (as written in his contract), but has put minimal effort into it. He has to lead the regular prayers. Otherwise, the people living near the pyramid would not get food from the automatic dispenser in the pyramid and would starve.

As he gets older, he teaches Yussuf to be the priest after he dies. Yussuf is a true believer and does not know the background story. He would not believe it even in the face of evidence.

The pyramid has just been found by the UN and they are confused. A pyramid near Berlin? So they send the protagonists to investigate.

At the same time, Farouk's ceremonial staff has run out of power (even though he keeps recharging it in the pyramid's central chamber). The firmware has been corrupted and he can no longer safely access the pyramid! The next cycle of rituals cannot continue. The food will not be distributed and everyone will starve.

The protagonists will have to enter the pyramid Indiana Jones style. With all the traps activated. And recharge and reflash the staff in the central chamber. Yussuf and Farouk will accompany them. And on this journey they will learn the origin of this pyramid.

In the end, they will decide the fate of many people.

\section{Character introduction}

\subsection{Lost}

Lost characters start the game in a camp with their extended families somewhere in the swamps around Berlin. They make their living hunting animals with their swamp boats and plundering ruins. A simple life. Close to nature and family. As they eat German gumbo and play their banjos, their radio operator receives a call from the UN asking for help and promising resource points as payment. Everyone wants those points, and a small delegation is sent to the meeting point in the Norm town of Gransee (and the Lost have never dared to go there before. The Norms are a strange group).
The protagonists jump into their diesel-powered old trucks and head for the city.

\subsection{Pioneers}

A long time ago there was a hacker camp with thousands of nerds. It was only supposed to last a week. But the catastrophes in the rest of the world motivated many of them to just stay there and build a pioneer settlement. Children were born and raised among soldering irons and technological experiments. Not knowing the world outside. The disaster about 10 years ago with the genetically modified chillies (a group of people wanted to turn them into ice cream using liquid nitrogen. There was a combustion) killed dozens and left a contaminated part of the camp inaccessible without protective equipment. They are still trying to make it accessible. Resource points to pay for non-renewable resources would be needed.

The Pioneers have a construction kit that allows them to build prototypes of Modular Individual Vehicles (MIVs) in a very short time. So they will arrive in Gransee in a very strange electric vehicle.

\subsection{Norms}

Norms live in fully automated cities called Hives. The Gransee Hive is quite small. The old buildings still exist, but they have been turned into a kind of museum, while the modern architecture has been built around them. The Hive Seed AI is large enough to coordinate all the people and their Hive Controllers. But the range of the wifi is quite limited and will never reach the pyramid!
The Ceres, which provides lab-grown food, is also small. They only have one processing line that produces fresh fruit pulp from stem cells. That is why the message is going around to eat more banana. Food is free anyway. But there are still more than 50 5-litre containers of banana pulp to be distributed before the production line can move on to the next fruit (raspberries). So this is an emergency!
Transport is by public transport (3 types of coach: Those with a café, some with restaurants, type three has a playground and a small room for the parents) and individual vehicles have to be parked outside the city.
Everyone has a Hive Controller to stay connected to each other and the AI. You can access all information and control everything. Visitors have guest controllers. But they start off in child mode and need a tutorial before all the features are available. And a medical exam before you can order alcohol and coffee.

Norm players will be asked to host the UN meeting. It will take place in Ceres. Please decorate a room (the UN decorations are in a box in the attic). And pick up the guests. They will be confused. Distribute the Hive Controllers and make sure the Lost and the Pioneers get along with the civilised humans.


\section{The UN meeting}

There is a video conference with an African woman called Diya from the UN. The connection is bad - the satellite network was broken more than 10 years ago. She explains that UN drones searching for survivors have found something strange near Berlin. A pyramid - 1 metre taller than the Cheops pyramid - and a small village plus a temple. There seem to be people there, and they look starving. The UN needs feet on the ground to investigate. As payment, everyone gets resource points to spend on non-renewable resources.

\section{After the UN meeting}

Before they leave, they might remember to order a Hive Repeater from the Library of Things. After the adventure, they will need to bring it back - undamaged and unaltered. However, the repeater would extend the hive's range to the pyramid if placed between the hive and the pyramid. Ordering a pizza with a flying drone will take about 1 hour to get to the pyramid - but it can be done. There will be no Hive reception in the Pyramid. The walls are thick.

\section{Finding the pyramid}

The biosphere reserve east of Gransee is treeless. After the catastrophes, it is muddy with a few tree stumps sticking out into the sky. The pyramid is in a valley, surrounded by some "old Egyptian" houses and a temple. Some fields grow rice (not enough). A canal for reed boats leads from the pyramid through the village. This waterway is used for the automatic distribution of food (after each ceremony).

The pyramid is in the centre.

\section{Entering the area}

Once there, they encounter an ancient Egyptian slum. The simulated "Nile" flows idly between the few fields and houses. The ordinary people who live there are shocked by the visitors' appearance. When the high priest Faroul (80 years old) sees them, he tries to lead them quickly and surreptitiously into his temple and the living room attached to it. He wants to brief them before they start talking to the people or to Yussuf.

He speaks normally to visitors and knows a lot about technology - he lived in Berlin before the disaster. For rituals, he will speak Swabian - the holy language.

(He invented this whole religion many years ago. With his Swabian background and his focus on hacking this religion together as quickly as possible, this was the best choice. Fulfilling the contract with minimal effort).

Farouk needs help. The storehouse in the pyramid will provide food after a ritual is celebrated. But his ceremonial staff is broken. He suspects the battery is broken (but fixing it will also reveal a corrupted firmware). Without the staff, he cannot properly enter the pyramid. And in there is the charging/flashing station. Near the burial chamber.

\section{Into the pyramid}

The protagonists can sneak into the pyramid through the main entrance. Or they can be introduced by Farouk as pilgrims from afar, paying their respects to the New Ra. Either way, Farouk and Yussuf will enter the pyramid with them. Farouk has already been to the inner sanctum. But for Yussuf this is the journey to enlightenment. Which will most likely end in confusion and a shattered worldview. Which makes him the final boss.

Upon entering the pyramid, Farouk will notice differences from his normal trips into the pyramid. Without the Bluetooth handshake from his staff, direct paths are blocked. Instead, adventurers will learn that traps have been activated - soon.

After passing through the large stone doors, they will close automatically. Radio frequencies (to the Hive!) will be blocked by the thick stone walls.

A few more steps and someone will trigger the first trap.

\section{A warning}

A trapdoor in the ceiling suddenly opens and a skeleton falls out. It dangles in front of a shocked adventurer. The skeleton is made of plastic. With fake and real spider webs. A sign in its hands reads "Traps activated. Turn around or die". The locked doors only allow option 2.

If the protagonists examine the small room in the ceiling where it was stored, they will find a small badge: "Ticket ID: 234786".

\section{The trip through the pyramid}

While sneaking through the maze of the pyramid (Farouk: "It was straight up! Where did this labyrinth come from?"), the protagonists will come across several traps. The engineers have designed them to be as safe as possible, while respecting the contract. The ticket IDs on each track can later be linked to a description in project management software.

Take as many traps as you like. Maybe skip some.

\subsection{Trap: rolling stones}

The adventurers will descend a ladder into a pit. This pit leads forward and up. This must be the way to the centre of the pyramid (and it is). Directly to their right is a strange system. There is a small room behind iron bars containing a huge boulder. And a broken trigger mechanism. If a protagonist should repair it, it will turn out to be a lift for the boulder. And the boulder will be lifted up.
A minute later, the bars will open. The lift is back without the boulder. And the rolling-crashing-dropping sounds can be heard getting closer. This is a giant marble track, and the boulder will crush the protagonists. For safety, there are flashing warning signs on the ceiling. There are also alcoves every few metres along the track where the adventurers can avoid the boulder.
When the boulder reaches the end of the track, it will roll into the lift. The bars will close and the boulder will be lifted back to the start.
The trap is easy to survive once the protagonists understand it. But a trap with warning signs and escape routes should confuse them.

The badge inside the lift reads "Ticket ID: 98798123"

By the way: Not repairing the broken lift makes this part of the journey a piece of cake.

\subsection{Trap: arrow trap}

The floor for the next 10 metres is covered with large stone slabs. Each stone has a letter of the alphabet engraved on it. To cross it, you have to jump over the stones in a certain pattern. If you step on the wrong letter, you trigger the mechanism. Dozens of arrows - foam arrows, Nerf style - will be fired.

(The specifications did not specify which arrows to use. So the engineers chose soft ones.)

The trick is to identify the correct letters: All the letters are written in Comic Sans. Except for the letter X, which is in a strange font. A typography expert can help here. Jump from X to X. Or get hit by annoying arrows. On the other side is a plaque: "Ticket ID: 1254356"

\subsection{Hint: The New Ra}

A painting (Egyptian style) on the wall shows a man driving a sports car on a beach. With palm trees and the sea in the background. Long, blond, curly hair blowing in the wind.

Farouk: This is the New Ra. While he was still human
Yussuf, praying: In his vessel of flesh and blood. Like us mortals. Before he shed his skin and ascended

\subsection{Trap: trapdoor and spikes}

Suddenly a trapdoor opens beneath the protagonists. They fall 10 cm. They might sprain an ankle. The fall stops at wooden spikes. Tennis balls are stuck on the spikes. For safety reasons.

A badge reads: "Ticket ID: 987345"

\subsection{Hint: The rise of the New Ra}

A new picture on the wall (old Egyptian style) shows the car of Ra crashing into a pine tree. A ball of fire and the lifeless body of Ra rising into the sky. His spirit rises towards the sun.

Yussuf (filled with devotion): This is where the New Ra sacrificed himself on a tree for us.

Farouk: It must have happened here somewhere. The pyramid was built on the site of the event.


\subsection{Trap: Fire Columns}

Turning a corner, the protagonists are confronted by flickering columns of fire shooting up from the floor to the ceiling. They seem to be dancing to some silent music.
It might be possible to walk through it - if you know the pattern.

Someone with history skills might be able to identify the silent song - playing it loudly or singing it will make it easy to dance through.

Maybe it won't surprise anyone that the song is "Never gonna give you up".

The badge on the other side reads: "Ticket ID: 97867234"

There is also a red emergency button for switching off. And a fire extinguisher. And a first aid kit.

\subsection{Entrance to the burial chamber}

The adventurers should now be quite confused by the strange traps playing nice. Soon they will learn the truth.

They stand at the end of the passage. In front of a majestic door. On the left is a socket where the Staff of Ra can be placed to recharge and reflash. Which Farouk will do immediately. The door will not open yet - as the process is not yet complete.
On the other side of the corridor is a tapestry. This is the first time you will come across cloth. Pushing it aside reveals a boring metal door. A sign reads 'Control Room'.

\subsection{Control room}

The hidden control room was central to the final stages of pyramid construction (especially the traps). It was also used to control the burial ceremony.

But it was also home to nerdy techies. Bored. Disgusted with their tasks. Trying to create psychological outlets.

There is a dartboard with a photo of a guy with curly blond hair as a target. The face is unrecognisable - too many holes.
An expensive coffee machine, a fridge and a pile of soft drinks and energy drinks, all food covered in mould.

The computers are still working and can be switched on. Passwords are written on sticky notes under the keyboard or on a whiteboard. Nobody cared - it seems.

Examining the computers, you find many todos in the ticket system. All of them can be identified by the ticket numbers on the traps. Reading the discussion, no one was ever motivated to build real traps. Just fulfil the contract and keep it safe - so nobody gets hurt.
The protagonists can learn new swear words and insults from the entries. No one was interested in serving the "F*** Ra".

In a cardboard box in the corner there are new staffs of Ra. Still wrapped in plastic. Just in case the original staff fails to update.

You can also log into a computer and open the burial chamber. The default music is set to "Also sprach Zarathustra". Of course.

Yussuf should already be close to snapping, and seeing this room might trigger it.

\subsection{Burial chamber}

In the centre of the room is a golden sarcophagus. Opening the lid reveals a well-preserved mummy in astronaut clothing. The face (destroyed in the crash) is covered by a golden mask. It looks very much like the visor of a Marvel superhero. There are golden rays of sunlight around the head. They look like hair.

There are rows of chairs, as if for a presentation or a speech. This seems to be how the Lemmings used to celebrate in the old days. A screen is rolled down for a Powerpoint presentation. It starts automatically.
It shows the life of the New Ra. Lots of money (the older ones will recognise this). Yachts. Rockets. Private submarines. Pools. But somehow no one learns more about the deceased.
The end of the powerpoint seems to be a tribute: A man in a suite (with golden hair) lifting rockets and other men in suits to the stars.

When the protagonists turn around, they see many glass cases filled with merchandise from science fiction shows. Starship models. Uniforms. A bat'leth from Star Trek, daggers, phasers. Everything is fake. The bladed weapons are still dangerous. Older protagonists can recognise them. Maybe some Lost with their historical leanings, or Norms from long-running series.

This is where Yussuf will snap. If no one intervenes. He will grab a bladed weapon and attack everyone. He tries to get the Staff of Ra. His worldview has just been shattered.

Fighting is one option. Or use the SFX equipment in the tech room as the voice of God.

\subsection{Decisions}

Having dealt with Yussuf in one way or another, the protagonists will have to find a solution for Farouk, Yussuf and the people who live here. The SFX equipment in the control room may come in handy. Maybe they can spin some legends or reprogram the system.

This debate is the real showdown, and it will involve difficult moral choices.

\section{Back to the Hive}

This adventure will end in the Ceres of the Gransee Hive. There is still banana left. But also the next fruit, raspberry and ice cream. The UN has its post-mortem and everyone can relax. Maybe some people like Farouk and Yussuf will join them on their first trip to a new civilisation.

\section{NPCs}

\newpage

\begin{npcBox}[title=Farouk]

    \begin{aspects}
    \item \aspect[High Concept]{Aging priest of an invented religion}
    \item \aspect[Trouble]{I do not believe, but I act - for the people}
    \item \aspect[Aspect]{Yussuf is like my own son}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{4}
        \item \nskill{Athletics}{0}
        \item \nskill{Burglary}{0}
        \item \nskill{Contacts}{1}
        \item \nskill{Crafts}{1}
        \item \nskill{Deceive}{2}
        \item \nskill{Drive}{0}
        \item \nskill{Empathy}{2}
        \item \nskill{Fight}{0}
        \item \nskill{Investigate}{0}
        \item \nskill{Lore}{1}
        \item \nskill{Notice}{2}
        \item \nskill{Physique}{0}
        \item \nskill{Provoke}{0}
        \item \nskill{Rapport}{3}
        \item \nskill{Resources}{1}
        \item \nskill{Shoot}{0}
        \item \nskill{Stealth}{0}
        \item \nskill{Will}{3}
     \end{skills}

    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}
    Farouk is 80 years old and the high priest of the New Ra religion. He also created it. Now all he wants is for everyone to be safe. For that, the rituals must continue. His plan (until the PCs arrive) is to make Yussuf the new High Priest. The name he was born with is "Martin Eisele", from the South German region of Swabia.
    He is a nice guy and a mentor/father figure for Yussuf.

    \end{npcDescription}

\end{npcBox}

\newpage

\begin{npcBox}[title=Yussuf]

    \begin{aspects}
    \item \aspect[High Concept]{True believer and almost ready to become the High Priest}
    \item \aspect[Trouble]{My world view is rock solid and will shatter if challenged}
    \item \aspect[Aspect]{Doubts that Farouk is a true believer}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{0}
        \item \nskill{Athletics}{4}
        \item \nskill{Burglary}{0}
        \item \nskill{Contacts}{0}
        \item \nskill{Crafts}{0}
        \item \nskill{Deceive}{0}
        \item \nskill{Drive}{0}
        \item \nskill{Empathy}{1}
        \item \nskill{Fight}{3}
        \item \nskill{Investigate}{0}
        \item \nskill{Lore}{1}
        \item \nskill{Notice}{1}
        \item \nskill{Physique}{2}
        \item \nskill{Provoke}{0}
        \item \nskill{Rapport}{2}
        \item \nskill{Resources}{0}
        \item \nskill{Shoot}{2}
        \item \nskill{Stealth}{1}
        \item \nskill{Will}{0}
     \end{skills}

    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}
    Yussuf is a 20-year-old follower of the New Ra. He grew up in the "Egyptian" village and knows nothing of the outside world. For Farouk, he is more than just an apprentice. Farouk treats him like a son. Yussuf does not take well to the shattering of his world view.
    \end{npcDescription}

\end{npcBox}

\newpage

\section{Player characters}

This is a con adventure. The characters do not have faction-specific skills to make it easier.
\newpage

\begin{npcBox}[title=Norm: Sam]

    \begin{aspects}
    \item \aspect[High Concept]{Fidgety typographer for concert flyers}
    \item \aspect[Trouble]{Excited and hyperactive - sometimes things can get broken}
    \item \aspect[Aspect]{Hey ! Watch me ! High Kick !}
    \item \item \aspect[Aspect]{Coffee - for thinking, need coffee}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{3}
        \item \nskill{Athletics}{1}
        \item \nskill{Burglary}{0}
        \item \nskill{Contacts}{3}
        \item \nskill{Crafts}{0}
        \item \nskill{Deceive}{0}
        \item \nskill{Drive}{0}
        \item \nskill{Empathy}{0}
        \item \nskill{Fight}{1}
        \item \nskill{Investigate}{4}
        \item \nskill{Lore}{0}
        \item \nskill{Notice}{2}
        \item \nskill{Physique}{1}
        \item \nskill{Provoke}{0}
        \item \nskill{Rapport}{1}
        \item \nskill{Resources}{2}
        \item \nskill{Shoot}{0}
        \item \nskill{Stealth}{0}
        \item \nskill{Will}{2}
     \end{skills}

    \begin{stunts}
    \item \stunt{Like Chug Novice !}{My hobby is Kung Fu. I get +2 when using it in a fight.}
    \end{stunts}



    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}

    Typographer for concert flyers. And has plenty of time for the Kung Fu hobby.

    Tool info: Has a Hive controller at the side of the head which can also be used as a headlight.

    \end{npcDescription}

\end{npcBox}

\newpage

\begin{npcBox}[title=Norm: Chris]

    \begin{aspects}
    \item \aspect[High Concept]{Cthulhu Game Master without snooze button}
    \item \aspect[Trouble]{Will warp everything mysterious into horror tropes and stories}
    \item \aspect[Aspect]{Dangerous half-knowledge about history}
    \item \item \aspect[Aspect]{No one expects my sleight of hand}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{2}
        \item \nskill{Athletics}{0}
        \item \nskill{Burglary}{1}
        \item \nskill{Contacts}{0}
        \item \nskill{Crafts}{0}
        \item \nskill{Deceive}{3}
        \item \nskill{Drive}{0}
        \item \nskill{Empathy}{0}
        \item \nskill{Fight}{0}
        \item \nskill{Investigate}{2}
        \item \nskill{Lore}{0}
        \item \nskill{Notice}{1}
        \item \nskill{Physique}{0}
        \item \nskill{Provoke}{1}
        \item \nskill{Rapport}{4}
        \item \nskill{Resources}{1}
        \item \nskill{Shoot}{0}
        \item \nskill{Stealth}{1}
        \item \nskill{Will}{2}
     \end{skills}

    \begin{stunts}
    \item \stunt{The walls are closing in}{Gets +2 on intimidation if the environment can be wrapped into a horror story}
    \end{stunts}



    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}

        As a Norm, Chris does not need a job. Chris uses all spare time to entertain people by GM-ing Cthulhu Pen and Paper roleplaying games. Chris' knowledge of history is based on made-up history for horror games.

    Tool info: Has a Hive controller at the side of the head which can also be used as a headlight.

    \end{npcDescription}

\end{npcBox}

\newpage

\begin{npcBox}[title=Pioneer: Fixit]

    \begin{aspects}
    \item \aspect[High Concept]{Hardware tinkering Nerd}
    \item \aspect[Trouble]{Leaves nothing broken unrepaired}
    \item \aspect[Aspect]{Images of old PCBS and schematis are gold}
    \item \item \aspect[Aspect]{Better than new}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{3}
        \item \nskill{Athletics}{1}
        \item \nskill{Burglary}{1}
        \item \nskill{Contacts}{0}
        \item \nskill{Crafts}{4}
        \item \nskill{Deceive}{0}
        \item \nskill{Drive}{2}
        \item \nskill{Empathy}{0}
        \item \nskill{Fight}{0}
        \item \nskill{Investigate}{3}
        \item \nskill{Lore}{0}
        \item \nskill{Notice}{1}
        \item \nskill{Physique}{1}
        \item \nskill{Provoke}{0}
        \item \nskill{Rapport}{0}
        \item \nskill{Resources}{2}
        \item \nskill{Shoot}{2}
        \item \nskill{Stealth}{0}
        \item \nskill{Will}{0}
     \end{skills}

    \begin{stunts}
    \item \stunt{Laser guided rocks}{Using my tuned slinghshot I get +2 on shooting.}
    \end{stunts}



    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}

    Fixit is always tinkering. Repairing and improving existing equipment is Fixit's life.

    Tool info: OLEDs integrated into the clothing can shine light in all colours. Even animated light effects are possible..

    \end{npcDescription}

\end{npcBox}

\newpage


\begin{npcBox}[title=Pioneer: Drop-and-run]

    \begin{aspects}
    \item \aspect[High Concept]{Decontamination specialist at the DOC (Decontamination Operation Centre)}
    \item \aspect[Trouble]{Hypochondriac and paranoid - the reason D-A-R is still alive}
    \item \aspect[Aspect]{I extend my protective instinct to cover my friends}
    \item \item \aspect[Aspect]{...but a fearless driver...}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{1}
        \item \nskill{Athletics}{3}
        \item \nskill{Burglary}{1}
        \item \nskill{Contacts}{0}
        \item \nskill{Crafts}{4}
        \item \nskill{Deceive}{0}
        \item \nskill{Drive}{3}
        \item \nskill{Empathy}{0}
        \item \nskill{Fight}{0}
        \item \nskill{Investigate}{1}
        \item \nskill{Lore}{0}
        \item \nskill{Notice}{2}
        \item \nskill{Physique}{2}
        \item \nskill{Provoke}{0}
        \item \nskill{Rapport}{0}
        \item \nskill{Resources}{1}
        \item \nskill{Shoot}{0}
        \item \nskill{Stealth}{0}
        \item \nskill{Will}{2}
     \end{skills}

    \begin{stunts}
    \item \stunt{The Rincewind}{When fleeing from danger I get +2 on Athletics.}
    \end{stunts}



    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}

    As a child D-A-R experienced and survived the Chili-and-liquid-nitrogen disaster. There D-A-Rs focus for safety was born.

    Tool info: OLEDs integrated into the clothing can shine light in all colours. Even animated light effects are possible..

    \end{npcDescription}

\end{npcBox}

\newpage


\begin{npcBox}[title=Lost: Falko]

    \begin{aspects}
    \item \aspect[High Concept]{History nerd between books and gramophone records}
    \item \aspect[Trouble]{Loves to share catchy tunes and songs}
    \item \aspect[Aspect]{Lets set up a radio and ask the ether. One of my friends will know more.}
    \item \item \aspect[Aspect]{Another lock picked}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{4}
        \item \nskill{Athletics}{1}
        \item \nskill{Burglary}{3}
        \item \nskill{Contacts}{0}
        \item \nskill{Crafts}{0}
        \item \nskill{Deceive}{1}
        \item \nskill{Drive}{1}
        \item \nskill{Empathy}{0}
        \item \nskill{Fight}{2}
        \item \nskill{Investigate}{2}
        \item \nskill{Lore}{0}
        \item \nskill{Notice}{1}
        \item \nskill{Physique}{0}
        \item \nskill{Provoke}{0}
        \item \nskill{Rapport}{3}
        \item \nskill{Resources}{0}
        \item \nskill{Shoot}{0}
        \item \nskill{Stealth}{2}
        \item \nskill{Will}{0}
     \end{skills}

    \begin{stunts}
    \item \stunt{Thieving}{Gets +2 on Burglary when picking locks}
    \end{stunts}



    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}

    Has incredible knowledge in recent history. Especially the music between 1970 to 2000.

    Tool info: Can improvise a torch very quick.

    \end{npcDescription}

\end{npcBox}


\newpage


\begin{npcBox}[title=Lost: Rocky]

    \begin{aspects}
    \item \aspect[High Concept]{The back like a wardrobe, with a sledge hammer and a six pack of beer.}
    \item \aspect[Trouble]{A rough demeanour only partially masks the emotional side}
    \item \aspect[Aspect]{Break-ins, excavations and demolitions}
    \item \item \aspect[Aspect]{Actions instead of big talk}
    \end{aspects}

    \begin{skills}
        \item \nskill{Academics}{0}
        \item \nskill{Athletics}{3}
        \item \nskill{Burglary}{0}
        \item \nskill{Contacts}{0}
        \item \nskill{Crafts}{1}
        \item \nskill{Deceive}{0}
        \item \nskill{Drive}{1}
        \item \nskill{Empathy}{1}
        \item \nskill{Fight}{2}
        \item \nskill{Investigate}{0}
        \item \nskill{Lore}{0}
        \item \nskill{Notice}{3}
        \item \nskill{Physique}{4}
        \item \nskill{Provoke}{2}
        \item \nskill{Rapport}{0}
        \item \nskill{Resources}{1}
        \item \nskill{Shoot}{2}
        \item \nskill{Stealth}{0}
        \item \nskill{Will}{0}
     \end{skills}

    \begin{stunts}
    \item \stunt{I see you}{Can use Notice instead of Empathy to judge a person Rocky knows for more than one hour.}
    \end{stunts}



    \begin{stressSection}
    \stressLine{\stress{1}\stress{1}\stress{1}}{\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}\stress{1}}
    \end{stressSection}
    \begin{tabularx}{\textwidth}{ XX }
    \end{tabularx}

    \begin{consequences}
    \item \consequence{2}
    \item \consequence{4}
    \item \consequence{6}
    \end{consequences}

    \begin{npcDescription}

    Hard as a rock - with plenty of hidden emotions.

    Tool info: Can improvise a torch very quick.

    \end{npcDescription}

\end{npcBox}

\newpage



\section{Potential story hooks}

After this adventure, the world may contain a cult of the New Ra. The protagonists could be rehired by the UN for further missions in the swamplands around Berlin.... and Berlin - what happened to it during the catastrophes?

\section{Experience with player behaviour}

\begin{itemize}
    \item One group chose the evil path: They made the followers of the New Ra dependent on constant supplies from the hive, and received regular resource points from the UN. In a campaign, I would put these characters in NPC mode and make them the villains for the next few adventures.
    \item Another group integrated the faithful into the Hive. After a ceremonial procession with the sarcophagus to the Hive - and safety. One year later: The doorbell rings: "Do you want to talk about the New Ra? Now there is a mummy cult in northern Germany.
    \item One group skipped the boss fight. When Rocky realised Yussuf was going off the rails, Rocky gave him a therapeutic bear hug. Preventing escalation.
\end{itemize}


\section{Customizing this adventure}

\subsection{Location}
This story is happening close to Berlin, at Zehdenick/Gransee area. With minor adjustments you can place it somewhere else.

\subsection{Languages}
The sacred language is the Swabian dialect. If you can speak it: perfect. It is the dialect right from the other side of Germany - far away from Berlin. To people in Berlin it will sound rural. Maybe you can use some equivalent.

\subsection{Motivation}

* When playing with other characters one protagonist could know Farouk from before the disaster and receive an emergency call from him.
